---
title: "Water Chemistry"
author: "AES Technical"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r libraries}
# import libraries
library(tidyverse)
library(broom)
library(kableExtra)
```

## Summary Charts of Water Chemsitry Data RW4 95^th^ st. 2022

```{r data_import}

# import data
water_chem <- read.csv("data/water_chem.csv")

rainfall <- read.csv("data/rain_aet.csv") %>%
  mutate(date = as.Date(date))

primo.water <- read.csv("data/primo_water_21.csv")
```

``` {r data_clean}

# clean up spreadsheet
water_chem <- water_chem %>%
  mutate(DATE = as.Date(DATE, origin = "1899-12-30"),
         pH = as.numeric(str_replace(pH, "-", "")),
         Tempmax = str_replace(Tempmax, "-", ""),
         Tempmax = as.numeric(str_replace(Tempmax, ",", ".")),
         Feed = as.numeric(str_remove_all(Feed, "[:alpha:]|\\s")),
         Solids = as.numeric(str_remove_all(Solids, "[:alpha:]|\\s|\\(|\\)|\\-")),
         Settling.Tank = str_to_lower(Settling.Tank),
         Foam.Level = as.numeric(str_remove_all(Foam.Level, "[:alpha:]|\\/|\\s")))
```

``` {r data_mutate}

# mutate some useful parameters
water_chem_4 <- water_chem %>%
  filter(DATE > "2021-12-31") %>%
  mutate(batch = case_when(DATE < "2022-02-17" ~ "batch_1",
                           DATE >= "2022-02-17" & DATE <= "2022-08-18" ~ "batch_2",
                           DATE >= "2022-08-20" & DATE <= "2022-11-30" ~ "batch_3"),
         total.feed = Feed * 8,
         Nitrite = case_when(Nitrite > 100 ~ Nitrite / 1000,
                             TRUE ~ Nitrite),
         pH = replace(pH, pH > 14, NA_real_),
         Settling.Tank = case_when(Settling.Tank == "no" ~ 0,
                                   Settling.Tank == "yes" ~ 1,
                                   TRUE ~ 0))


```

## TAN

``` {r tan, fig.cap = "TAN levels in RW 4 2022.", fig.align = "center"}

# plot TAN
rw_4_tan <- water_chem_4 %>%
  ggplot(aes(DATE, TAN, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "TAN (mg/l)") + 
  theme_minimal()

rw_4_tan
```

## Nitrite

``` {r nitrite, fig.cap = "Nitrite levels in RW 4 2022.", fig.align = "center"}

# plot nitrite
rw_4_nit <- water_chem_4 %>%
  ggplot(aes(DATE, Nitrite, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Nitrite (mg/l)") + 
  theme_minimal()

rw_4_nit
```

## Alkalinity

``` {r alk, fig.cap = "Alkalinity levels in RW 4 2022.", fig.align = "center"}

# plot Alk
rw_4_alk <- water_chem_4 %>%
  ggplot(aes(DATE, ALK, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Alkalinity (mg/l)") + 
  theme_minimal()

rw_4_alk
```

## pH

``` {r ph, fig.cap = "pH levels in RW 4 2022.", fig.align = "center"}

# plot pH
rw_4_ph <- water_chem_4 %>%
  ggplot(aes(DATE, pH, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "pH") + 
  theme_minimal()

rw_4_ph
```

## Salinity

``` {r salinity, fig.cap = "Salinity levels in RW 4 2022.", fig.align = "center"}

# plot salinity
rw_4_sal <- water_chem_4 %>%
  ggplot(aes(DATE, Salinity, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Salinity (ppt)") + 
  theme_minimal()

rw_4_sal
```

## Dissolved Oxygen

``` {r oxygen, fig.cap = "Dissolved oxygen levels in RW 4 2022.", fig.align = "center"}

# plot DO
rw_4_do <- water_chem_4 %>%
  ggplot(aes(DATE, DOmin, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "DO min (mg/l)") + 
  theme_minimal()

rw_4_do
```

## Solids

``` {r solids, fig.cap = "Solids levels in RW 4 2022.", fig.align = "center"}

# plot solids
rw_4_solids <- water_chem_4 %>%
  ggplot(aes(DATE, Solids, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Solids (ml)") + 
  theme_minimal()

rw_4_solids
```

## Settling Tank Operation

``` {r settling, fig.cap = "Settling tank operation in RW 4 2022.", fig.align = "center"}

# plot settling tank
rw_4_settling <- water_chem_4 %>%
  ggplot(aes(DATE, Settling.Tank, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Settling Tank (1/0)") + 
  theme_minimal()

rw_4_settling
```

During 2022 the settling tank in RW4 was operated for a total of `r sum(water_chem_4$Settling.Tank)` days from a production period of `r length(water_chem_4$Settling.Tank)` days. Total discharge water from this settling tank was `r sum(water_chem_4$Settling.Tank) * 2` m^3^. Average water use for solids removal from RW4 `r format(sum(water_chem_4$Settling.Tank) * 2 / length(water_chem_4$Settling.Tank), digits = 3)` m^3^/day.

## Total Feed Input

``` {r feed, fig.cap = "Total daily feed input in RW 4 2022.", fig.align = "center"}

# plot total feed
rw_4_feed <- water_chem_4 %>%
  ggplot(aes(DATE, total.feed / 1000, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Total Feed (kg)") + 
  theme_minimal()

rw_4_feed
```

## Estimated Nitrate levels bsed on cumulative Nitrite calculation

``` {r cumulative_nitrate}

# estimate cumulative nitrate based on nitrite production
cumulative.nitrate.95 <- water_chem_4 %>%
  mutate(total.volume = 90000 * Water.Level / 36,
         total.nitrite = Nitrite * total.volume) %>%
  group_by(batch) %>%
  mutate(cs = cumsum(total.nitrite),
         cumulative.nitrate = cs / total.volume)
```

``` {r nitrate, fig.cap = "Estimated nitrate levels in RW 4 2022.", fig.align = "center"}

# plot cumulative nitrate
rw_4_nitrate <- cumulative.nitrate.95 %>%
  ggplot(aes(DATE, cumulative.nitrate, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Cumulative Nitrate (mg/l)") + 
  theme_minimal()

rw_4_nitrate
```

``` {r rainfall_plot, fig.cap = "Mean monthly precipitation/ evapo-transpiration rates for Blue Cypress Lake, Florida, USA.", fig.align = "center"}
# custom color
rain.cols <- c(rainfall = "#a6bddb", aet = "#045a8d")

rainfall %>%
  ggplot(aes(date, measure_in, color = condition)) +
  geom_line() +
  scale_color_manual("", breaks = c("rainfall", "aet"),
                     values = c(rain.cols),
                     labels = c("Rainfall", "AET")) +
  labs(x = "Date", y = "Precipitation/ Evapo-transpiration (Inches)") + 
  theme_minimal()
```

``` {r primo_water_21}

primo.water.21 <- primo.water %>%
  mutate(vol.cube = vol_gal / 0.26417205235815 / 1000)
```

``` {r primo_water_plot}
month.order <- c("January", "February", "March", "April",
                 "May", "June", "July", "August",
                 "September", "October", "November", "December")

primo.water.21 %>%
  ggplot(aes(factor(Month), vol.cube)) +
  geom_col(color = "#045a8d",fill =  "#a6bddb") +
  scale_x_discrete(limits = month.order, labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")) +
  labs(x = "", y = "Monthly water demand (m^3)") + 
  theme_minimal()
```

