---
title: "Fellsmere AES Supporting Material"
author: "AES Technical"
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
     fig_caption: yes
     number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r libraries}
# import libraries
library(tidyverse)
library(broom)
library(flextable)
library(kableExtra)
library(officer)
library(knitr)
```

``` {r initial_mass}
# define parameters
bw_0 <- 0.07
```

# Deliverables:

* Develop growth model
* Develop production plan
* Perform system mass balance equations
* Develop prototype system

***

# Growth Modeling

Growth model based on data supplied from SyAqua Americas 95^th^ st.facility.

**_Litopenaeus vannamei_** growth characteristics:

``` {r growth_data}

# import data
shrimp_growout <- read.csv("data/shrimp_growout.csv")

# find weight gain for weight midpoint
shrimp.growth <- shrimp_growout %>%
  mutate(wt.mid = (wt_2 + wt_1) / 2,
         g.gain.day = (wt_2 - wt_1) / (t_2 - t_1),
         geometric.mid = sqrt(wt_1 * wt_2))
```


```{r growth_model}

# try base code log-log relationship - looks good!
shrimp.fit.twinlog <- lm(log(g.gain.day) ~ log(wt.mid), data = shrimp.growth)

# calculate coefficients for growth curve bw_1 = [bw_0^c_1 + c_2 * days]^c_4
c_1 <- 1 - shrimp.fit.twinlog$coef[2]
c_2 <- c_1 * exp(shrimp.fit.twinlog$coef[1])
c_4 <- 1 / c_1

# try base code log-log relationship for geometric weight
shrimp.geometric.twinlog <- lm(log(g.gain.day) ~ log(geometric.mid), data = shrimp.growth)

# calculate coefficients for growth curve bw_1 = [bw_0^c_1 + c_2 * days]^c_4
geometric_c_1 <- 1 - shrimp.geometric.twinlog$coef[2]
geometric_c_2 <- c_1 * exp(shrimp.geometric.twinlog$coef[1])
geometric_c_4 <- 1 / geometric_c_1
```

```{r GrowthModelPlot, fig.cap = "Daily growth rate by mass - datapoints from SyAqua 95^th^st (blue - arithmetric model, black - geometric model).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# set some colours
cols <- c("quarantine" = "#bdc9e1", "nursery" = "#74a9cf", "juvenile" = "#2b8cbe", "growout" = "#045a8d")

# plot relationship between weight and grams gained per day 
p_shrimp_gain <- shrimp.growth %>%
  ggplot(aes(wt.mid, g.gain.day, color = phase)) +
  geom_point() +
  scale_color_manual(name = "Phase",
  labels = c("quarantine" = "Quarantine", "nursery" = "Nursery", "juvenile" = "Juvenile", "growout" = "Growout"),
  values = c(cols)) +
  stat_function(fun = function(x) exp(shrimp.fit.twinlog$coef[1]) * x^shrimp.fit.twinlog$coef[2], color = 'dodgerblue') +
  stat_function(fun = function(x) exp(shrimp.geometric.twinlog$coef[1]) * x^shrimp.geometric.twinlog$coef[2], color = 'black') +
  xlab("Mass (g)") +
  ylab("Daily mass gain (g/shrimp/day)") +
  theme_minimal()

p_shrimp_gain
```

***

From the growth model, an estimate of white-leg shrimp body mass - as a function of time from introduction - can be calculated.  
\n

``` {r bodyweight}

# estimate body-weight over time
bodyweight <- tibble(day = seq(1,180,1)) %>%
  mutate(bw = (bw_0^c_1 + c_2 * day)^c_4)

# import fellsmere growth data
fellsmere.growth <- read.csv("data/fellsmere_growth.csv")

# create model to incorporate fellsmere growth data
bodyweight.model <- bodyweight %>%
  mutate(data.source = "model") %>%
  bind_rows(fellsmere.growth)
```

``` {r ShrimpMassPlot, fig.cap = "Estimated shrimp mass at time from introduction (blue - arithmetic model, black - geometric model).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# shrimp growth model compared to fellsmere
shrimp.model.plot <- 
  bodyweight.model %>%
  ggplot(aes(day, bw, color = data.source)) +
  geom_line() +
  stat_function(fun = function(x) (bw_0^geometric_c_1 + geometric_c_2 * x)^geometric_c_4, color = 'black') +
  labs(x = "Day", y = "Mass (g)") +
  scale_color_discrete(name = "Data source", labels = c("Fellsmere", "Model")) +
  theme_minimal()

shrimp.model.plot
```

``` {r target_mass}

# define parameters
quarantine.max <- 1.2
nursery.max <- 3
juvenile.max <- 10
growout.max <- 32
nursery.harvest <- 5

shrimp.1_2.g <- ceiling(which(abs(bodyweight$bw - quarantine.max) == min(abs(bodyweight$bw - quarantine.max))))

shrimp.3.g <- ceiling(which(abs(bodyweight$bw - nursery.max) == min(abs(bodyweight$bw - nursery.max))))

shrimp.5.g <- ceiling(which(abs(bodyweight$bw - nursery.harvest) == min(abs(bodyweight$bw - nursery.harvest))))

shrimp.10.g <- ceiling(which(abs(bodyweight$bw - juvenile.max) == min(abs(bodyweight$bw - juvenile.max))))

shrimp.25.g <- ceiling(which(abs(bodyweight$bw - 25) == min(abs(bodyweight$bw - 25))))

shrimp.32.g <- ceiling(which(abs(bodyweight$bw - growout.max) == min(abs(bodyweight$bw - growout.max))))
```

Projected day to attain key bodyweights:

* Estimated growth day for `r quarantine.max`g shrimp: Day `r shrimp.1_2.g`
* Estimated growth day for `r nursery.max`g shrimp: Day `r shrimp.3.g`
* Estimated growth day for `r nursery.harvest`g shrimp: Day `r shrimp.5.g`
* Estimated growth day for `r juvenile.max`g shrimp: Day `r shrimp.10.g`
* Estimated growth day for `r growout.max`g shrimp: Day `r shrimp.32.g`

***

# Production Plan

``` {r harvest_targets}

harvest.95.1 <- 2200
harvest.95.2 <- 600

harvest.primo.1 <- 1200
harvest.primo.2 <- 1000
harvest.primo.3 <- 600

harvest.101.1 <- 1200
harvest.101.2 <- 600
harvest.101.3 <- 600

shrimp.harvest.day.32 <- as.integer(shrimp.32.g / 7) * 7
```

Review production plan(s) to achieve:

* 95^th^ st. 2022.Day `r shrimp.harvest.day.32` harvest `r harvest.95.1` individual `r growout.max`g shrimp per raceway.
* 95^th^ st. 2022. Day `r shrimp.harvest.day.32 + 14` harvest `r harvest.95.2` individual `r growout.max`g shrimp per raceway.

* 95^th^ st. 2023. Day `r shrimp.harvest.day.32` harvest `r harvest.primo.1` individual `r growout.max`g shrimp per raceway.
* 95^th^ st. 2023. Day `r shrimp.harvest.day.32 + 14` harvest `r harvest.primo.2` individual `r growout.max`g shrimp per raceway.
* 95^th^ st. 2023. Day `r shrimp.harvest.day.32 + 28` harvest `r harvest.primo.3` individual `r growout.max`g shrimp per raceway.

* 101^st^ st. Day `r shrimp.harvest.day.32` harvest `r harvest.101.1` individual `r growout.max`g shrimp per raceway.
* 101^st^ st. Day `r shrimp.harvest.day.32 + 14` harvest `r harvest.101.2` individual `r growout.max`g shrimp per raceway.
* 101^st^ st. Day `r shrimp.harvest.day.32 + 28` harvest `r harvest.101.3` individual `r growout.max`g shrimp per raceway.  

Definitions:  

* Phase - life stage or treatment process (Quarantine, Nursery, Juvenile, Growout, Depurate).  
* System - a single tank/ raceway in isolation or a group or tanks supported by a water processing unit.  
* Facility - collection of systems and phases in operation at same time (not including quarantine as located at separate facility). 

### System Occupation 95^th^st 2022:

``` {r system_occupation}
batch_frequency <- 30 # days between batches
batch_system_periods <- 1 # overall number of system periods
production_cycle <- 220 # period whose factor includes frequency, system period and exceeds minimum growout period
quarantine.period <- 29
nursery.period <- 30
juvenile.period <- 30
growout.period <- 120
depuration.period <- ceiling((harvest.95.1 + harvest.95.2) * 2 / 1600)
```

* Quarantine `r quarantine.period + 1` days.
* Nursery `r nursery.period` days.
* Juvenile `r juvenile.period` days.
* Grow-out up to `r growout.period` days.
* Depuration `r depuration.period` days.

``` {r prod_plan_95}

# set production period to two growth periods to observe system loading
prod_plan <- data.frame(facility_day = seq(0, 2 * production_cycle - 1)) %>%
  mutate(batch_1 = case_when(facility_day < production_cycle ~ facility_day))

for (lag_size in c(0:12)) {
  
  new_col_name <- paste0("lag.batch.", lag_size)
  
  prod_plan <- prod_plan %>%
    mutate(!!sym(new_col_name) := lag(batch_1, n = lag_size * batch_frequency, default = NA))
}

# remove column called batch_1
prod.plan <- prod_plan %>% select(-batch_1) %>%
  pivot_longer(c(lag.batch.0:lag.batch.12), names_to = "batch", values_to = "batch_day", values_drop_na = TRUE) %>%
  mutate(system = case_when(batch_day %in% c(0:quarantine.period) ~ "quarantine",
                            batch_day %in% c(quarantine.period + 1: nursery.period) ~ "nursery",
                            batch_day %in% c(quarantine.period + nursery.period + 1 : juvenile.period) ~ "juvenile",
                            batch_day %in% c(quarantine.period + nursery.period + juvenile.period + 1 : growout.period) ~ "growout",
                            batch_day %in% c(quarantine.period + nursery.period + juvenile.period + growout.period + 1 : depuration.period)  ~ "depurate")) %>%
  drop_na() %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.2", "lag.batch.5", "lag.batch.7", "lag.batch.10"))
```

``` {r System95Plot, fig.cap = "95^th^ st (2022). Production schematic.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# custom color
system_cols <- c(quarantine = "#d0d1e6", nursery = "#a6bddb", juvenile = "#74a9cf", growout = "#2b8cbe", depurate = "#045a8d")

systems_plot <- prod.plan %>%
  filter(batch_day <= production_cycle,
         batch %in% c("lag.batch.0", "lag.batch.2", "lag.batch.5", "lag.batch.7", "lag.batch.10")) %>%
  ggplot(aes(facility_day, batch, color = system)) +
  geom_line(size = 3) +
  scale_y_discrete(limits = c("lag.batch.0", "lag.batch.2", "lag.batch.5", "lag.batch.7", "lag.batch.10"),
                   labels = c("Batch 1", "Batch 2", "Batch 3", "Batch 4", "Batch 5")) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = "") + 
  theme_minimal()

systems_plot
```

## System Occupation 95^th^st 2023:

```{r system_occupation_primo}

# production plan primo 95
# define parameters
batch_frequency.primo <- 60 # days between batches
batch_system_periods.primo <- 1 # overall number of system periods
production_cycle.primo <- 220
quarantine.period.primo <- 29
nursery.period.primo <- 60
growout.period.primo <- 120
depuration.period.primo <- ceiling((harvest.95.1 + harvest.95.2) * 2 / 1600)
```

* Quarantine `r quarantine.period.primo + 1` days.
* Nursery `r nursery.period.primo` days.
* Grow-out up to `r growout.period.primo` days.
* Depuration `r depuration.period.primo` days.

``` {r prod_plan_primo}

# set primo production period to two growth periods to observe system loading
prod_plan_primo <- data.frame(facility_day = seq(0, 2 * production_cycle.primo - 1)) %>%
  mutate(batch_1 = case_when(facility_day < production_cycle.primo ~ facility_day))

for (lag_size in c(0:12)) {
  
  new_col_name <- paste0("lag.batch.", lag_size)
  
  prod_plan_primo <- prod_plan_primo %>%
    mutate(!!sym(new_col_name) := lag(batch_1, n = lag_size * batch_frequency.primo, default = NA))
}

# remove column called batch_1 from prod_plan_primo
prod.plan.primo <- prod_plan_primo %>% select(-batch_1) %>%
  pivot_longer(c(lag.batch.0:lag.batch.12), names_to = "batch", values_to = "batch_day", values_drop_na = TRUE) %>%
  mutate(system = case_when(batch_day %in% c(0:quarantine.period.primo) ~ "quarantine",
                            batch_day %in% c(quarantine.period.primo + 1 : nursery.period.primo ) ~ "nursery",
                            batch_day %in% c(quarantine.period.primo + nursery.period.primo + 1 : growout.period.primo) ~ "growout",
                            batch_day %in% c(quarantine.period.primo + nursery.period.primo  + growout.period.primo + 1 : depuration.period.primo)  ~ "depurate")) %>%
  drop_na()
```

``` {r SystemsPlotPrimo, fig.cap = "95^th^ st (2023). Production schematic.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# custom color
system_cols.primo <- c(quarantine = "#d0d1e6", nursery = "#a6bddb", growout = "#2b8cbe", depurate = "#045a8d")

systems_plot.primo <- prod.plan.primo %>%
  filter(batch_day <= production_cycle.primo,
         batch %in% c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6')) %>%
  ggplot(aes(facility_day, batch, color = system)) +
  geom_line(size = 3) +
  scale_y_discrete(limits = c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6'),
                   labels = c("Batch 1", "Batch 2", "Batch 3", "Batch 4", "Batch 5", "Batch 6", "Batch 7")) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "") + 
  theme_minimal()

systems_plot.primo
```

## System Occupation 101^st^st 2024:

``` {r system_occupation_101}

# production plan 101
# define parameters
batch_frequency.101 <- 60 # days between batches
batch_system_periods.101 <- 1 # overall number of system periods
production_cycle.101 <- 220
quarantine.period.101 <- 29
nursery.period.101 <- 60
growout.period.101 <- 120
depuration.period.101 <- ceiling((harvest.101.1 + harvest.101.2) * 6 / 1600)
```

* Quarantine `r quarantine.period.101 + 1` days.
* Nursery `r nursery.period.101` days.
* Grow-out up to `r growout.period.101` days.
* Depuration `r depuration.period.101` days.

``` {r prod_plan_101}

# set primo production period to two growth periods to observe system loading
prod_plan_101 <- data.frame(facility_day = seq(0, 2 * production_cycle.101 - 1)) %>%
  mutate(batch_1 = case_when(facility_day < production_cycle.101 ~ facility_day))

for (lag_size in c(0:12)) {
  
  new_col_name <- paste0("lag.batch.", lag_size)
  
  prod_plan_101 <- prod_plan_101 %>%
    mutate(!!sym(new_col_name) := lag(batch_1, n = lag_size * batch_frequency.101, default = NA))
}

# remove column called batch_1 from prod_plan_101
prod.plan.101 <- prod_plan_101 %>% select(-batch_1) %>%
  pivot_longer(c(lag.batch.0:lag.batch.12), names_to = "batch", values_to = "batch_day", values_drop_na = TRUE) %>%
  mutate(system = case_when(batch_day %in% c(0:quarantine.period.101) ~ "quarantine",
                            batch_day %in% c(quarantine.period.101 + 1 : nursery.period.101) ~ "nursery",
                            batch_day %in% c(quarantine.period.101 + nursery.period.101 + 1 : growout.period.101) ~ "growout",
                            batch_day %in% c(quarantine.period.101 + nursery.period.101  + growout.period.101 + 1 : depuration.period.101)  ~ "depurate")) %>%
  drop_na()
```

``` {r Systems101Plot, fig.cap = "101^st^ st (2024). Production schematic.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# custom color
system_cols.101 <- c(quarantine = "#d0d1e6", nursery = "#a6bddb", growout = "#2b8cbe", depurate = "#045a8d")

systems_plot.101 <- prod.plan.101 %>%
  filter(batch_day <= production_cycle.101,
         batch %in% c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6')) %>%
  ggplot(aes(facility_day, batch, color = system)) +
  geom_line(size = 3) +
  scale_y_discrete(limits = c('lag.batch.0', 'lag.batch.1', 'lag.batch.2', 'lag.batch.3', 'lag.batch.4', 'lag.batch.5', 'lag.batch.6'),
                   labels = c("Batch 1", "Batch 2", "Batch 3", "Batch 4", "Batch 5", "Batch 6", "Batch 7")) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "") + 
  theme_minimal()

systems_plot.101
```

***

# System Loading

``` {r shrimp_survival}
quarantine.in <- 35000
nursery.in <- 19500
juvenile.in <- 15000
growout.in <- 11000
growout.out <- 8800
depurate.in <- 1600

quarantine.survival <- 0.8
nursery.survival <- 0.8
juvenile.survival <- 0.8
growout.survival <- 0.8

```

Parameters used:

* Quarantine survival `r format(quarantine.survival * 100, scientific = FALSE, digits = 3)` %
* Nursery survival `r format(nursery.survival * 100, scientific = FALSE, digits = 3)` %
* Juvenile survival `r format(juvenile.survival * 100, scientific = FALSE, digits = 3)` % (95^th^st 2022 only)
* Growout survival `r format(growout.survival * 100, scientific = FALSE, digits = 3)` %

``` {r feed_model}

nursery.feed <- 0.05
growout.feed <- 0.04
depurate.feed <- 0

quarantine.protein <- 0.5
nursery.protein <- 0.4
juvenile.protein <- 0.4
growout.protein <- 0.35
depurate.protein <- 0.35

# import data
feed <- read.csv("data/feed.csv")

# filter phases of interest
quarantine.feed <- feed %>%
  filter(phase == "quarantine")

juvenile.feed <- feed %>%
  filter(phase == "juvenile")

juvenile.nursery.feed <- feed %>%
  filter(phase == "juvenile" | phase == "nursery")

quarantine.feed.twinlog <- lm(log(feed_pc) ~ log(wt), data = quarantine.feed)

juvenile.feed.log <- lm(log(feed_pc) ~ wt, data = juvenile.feed)

juvenile.nursery.feed.log <- lm(log(feed_pc) ~ wt, data = juvenile.nursery.feed)
```

``` {r facility_95}

quarantine.system.division <- 1
nursery.system.division <- 3
juvenile.system.division <- 1
growout.system.division <- 2
depurate.system.division <- 1
depurate.tanks <- 4

initial.stock <- 35000
```

## 95^th^ st. 2022 phase designations:

* Quarantine - initial population of `r format(initial.stock, scientific = FALSE)` individuals of body-weight `r bw_0` : `r quarantine.max`
* Nursery - divide `r format(nursery.in, scientific = FALSE)`, `r quarantine.max`g, shrimp between `r nursery.system.division` independently operating system(s), raise to `r nursery.max`g.
* Juvenile - rear `r format(juvenile.in, scientific = FALSE)`, `r nursery.max`g, shrimp within `r juvenile.system.division` system(s), raise to `r juvenile.max`g.
* Growout - rear `r format(growout.in, scientific = FALSE)`, `r juvenile.max`g, shrimp within `r growout.system.division` system(s), raise to `r growout.max`g.
* Depuration - purge up to `r format(depurate.in, scientific = FALSE)`, `r growout.max`g shrimp - split between `r depurate.tanks` tank(s), operated by `r depurate.system.division` treatment system(s).

``` {r system_loading_95}

# build system loading onto production plan
system.loading <- prod.plan %>%
  mutate(total.number = case_when(system == "quarantine" ~ initial.stock * exp(1)^(log(quarantine.survival) / quarantine.period * batch_day),
                                  system == "nursery" ~ nursery.in * exp(1)^(log(nursery.survival) / nursery.period * (batch_day - (quarantine.period + 1))),
                                  system == "juvenile" ~ juvenile.in * exp(1)^(log(juvenile.survival) / juvenile.period * (batch_day - (quarantine.period + 1) - nursery.period)),
                                  system == "growout" ~ growout.in * exp(1)^(log(growout.survival) / growout.period * (batch_day - (quarantine.period + 1) - nursery.period - juvenile.period)),
                                  system == "depurate" ~ depurate.in),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 ~ total.number - harvest.95.1 * growout.system.division, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 + 14 ~ 0, TRUE ~ total.number),
         process.number = case_when(system == "quarantine" ~ total.number / quarantine.system.division,
                                 system == "nursery" ~ total.number / nursery.system.division,
                                 system == "juvenile" ~ total.number / juvenile.system.division,
                                 system == "growout" ~ total.number / growout.system.division,
                                 system == "depurate" ~ total.number / depurate.system.division),
         bw = case_when(system == "depurate" ~ 32, TRUE ~ (bw_0^c_1 + c_2 * batch_day)^c_4),
         feed.rate = case_when(system == "quarantine" ~ exp(quarantine.feed.twinlog$coef[1]) * bw ^ quarantine.feed.twinlog$coef[2],
                               system == "nursery" ~ nursery.feed,
                               system == "juvenile" ~ exp(juvenile.feed.log$coef[1] + bw * juvenile.feed.log$coef[2]),
                               system == "growout" ~ growout.feed,
                               system == "depurate" ~ depurate.feed),
         protein.proportion = case_when(system == "quarantine" ~ quarantine.protein,
                                        system == "nursery" ~ nursery.protein,
                                        system == "juvenile" ~ juvenile.protein,
                                        system == "growout" ~ growout.protein,
                                        system == "depurate" ~ depurate.protein),
         total.bw.kg = bw * total.number / 1000,
         total.feed.kg = total.bw.kg * feed.rate,
         total.protein = total.feed.kg * protein.proportion,
         process.bw.kg = bw * process.number / 1000,
         process.feed.kg = process.bw.kg * feed.rate,
         process.protein = process.feed.kg * protein.proportion)
```

``` {r SystemIndividuals95, fig.cap = "Total number of individuals per phase (95^th^ st. 2022).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

system.n.95 <- system.loading %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, total.number, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in Batch") + 
  theme_minimal()

system.n.95
```

``` {r ProcessIndividuals95, fig.cap = "Total number of individuals per system (95^th^ st. 2022).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

tank.n.95 <- system.loading %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.number, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in System") + 
  theme_minimal()

tank.n.95
```

## 95^th^ st. 2023 phase designations:

``` {r facility_primo}

# system loading for primo
quarantine.in.primo <- 65000
nursery.in.primo <- 44000
growout.in.primo <- 16500
growout.out.primo <- 13200
depurate.in.primo <- 1600
nursery.harvest.primo <- 4000

harvest.primo.1 <- 1200
harvest.primo.2 <- 1000
harvest.primo.3 <- 600

quarantine.primo.division <- 1
nursery.primo.division <- 2
growout.primo.division <- 3
depurate.primo.division <- 1
depurate.tanks.primo <- 4
```

* Quarantine - initial population of `r format(quarantine.in.primo, scientific = FALSE)` individuals of body-weight `r bw_0` : `r quarantine.max`
* Nursery - divide `r format(nursery.in.primo, scientific = FALSE)`, `r quarantine.max`g, shrimp between `r nursery.primo.division` independently operating system(s), raise to `r juvenile.max`g.
* Growout - rear `r format(growout.in.primo, scientific = FALSE)`, `r juvenile.max`g, shrimp within `r growout.primo.division` system(s), raise to `r growout.max`g.
* Depuration - purge up to `r format(depurate.in.primo, scientific = FALSE)`, `r growout.max`g shrimp - split between `r depurate.tanks.primo` tank(s), operated by `r depurate.primo.division` treatment system(s).

``` {r system_loading_primo}

# build system loading onto production plan
system.loading.primo <- prod.plan.primo %>%
  mutate(total.number = case_when(system == "quarantine" ~ quarantine.in.primo * exp(1)^(log(quarantine.survival) / quarantine.period.primo * batch_day),
                                  system == "nursery" ~ nursery.in.primo * exp(1)^(log(nursery.survival) / nursery.period.primo * (batch_day - (quarantine.period.primo + 1))),
                                  system == "growout" ~ growout.in.primo * exp(1)^(log(growout.survival) / growout.period.primo * (batch_day - (quarantine.period.primo + 1) - nursery.period.primo)),
                                  system == "depurate" ~ depurate.in.primo),
         total.number = case_when(system == "nursery" & batch_day >= shrimp.5.g ~ total.number - nursery.harvest.primo * nursery.primo.division, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 ~ total.number - harvest.primo.1 * growout.primo.division, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 + 14 ~ total.number - harvest.primo.2 * growout.primo.division, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 + 28 ~ 0, TRUE ~ total.number),
         process.number = case_when(system == "quarantine" ~ total.number / quarantine.primo.division,
                                    system == "nursery" ~ total.number / nursery.primo.division,
                                    system == "growout" ~ total.number / growout.primo.division,
                                    system == "depurate" ~ total.number / depurate.primo.division),
         bw = case_when(system == "depurate" ~ 32, TRUE ~ (bw_0^c_1 + c_2 * batch_day)^c_4),
         feed.rate = case_when(system == "quarantine" ~ exp(quarantine.feed.twinlog$coef[1]) * bw ^ quarantine.feed.twinlog$coef[2],
                               system == "nursery" ~ exp(juvenile.nursery.feed.log$coef[1] + bw * juvenile.nursery.feed.log$coef[2]),
                               system == "growout" ~ growout.feed,
                               system == "depurate" ~ depurate.feed),
         protein.proportion = case_when(system == "quarantine" ~ quarantine.protein,
                                        system == "nursery" ~ nursery.protein,
                                        system == "growout" ~ growout.protein,
                                        system == "depurate" ~ depurate.protein),
         total.bw.kg = bw * total.number / 1000,
         total.feed.kg = total.bw.kg * feed.rate,
         total.protein = total.feed.kg * protein.proportion,
         process.bw.kg = bw * process.number / 1000,
         process.feed.kg = process.bw.kg * feed.rate,
         process.protein = process.feed.kg * protein.proportion)
```

``` {r SystemIndividualsPrimo, fig.cap = "Total number of individuals per phase (95^th^ st. 2023).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

system.n.primo <- system.loading.primo %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, total.number, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in Batch") + 
  theme_minimal()

system.n.primo
```

``` {r ProcessIndividualsPrimo, fig.cap = "Total number of individuals per system (95^th^ st. 2023).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

tank.n.primo <- system.loading.primo %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.number, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in System") + 
  theme_minimal()

tank.n.primo
```

## 101^st^ st. 2024 phase designations:

``` {r facility_101}

# system loading for 101
quarantine.in.101.a <- 65000
quarantine.in.101.b <- 100000
nursery.in.101.a <- 23000 * 2
nursery.in.101.b <- 23000 * 3
growout.in.101.a <- 5200 * 4
growout.in.101.b <- 5200 * 6
depurate.in.101 <- 1600
nursery.harvest.101 <- 4000

harvest.101.1 <- 1200
harvest.101.2 <- 600
harvest.101.3 <- 600

quarantine.101.division <- 1
nursery.101.division <- 2
growout.101.division.a <- 4
growout.101.division.b <- 2
growout.101.tank.multiplier <- 6
depurate.101.division <- 1
depurate.tanks.101 <- 4
```

* Quarantine - initial population of `r format(quarantine.in.101.a, scientific = FALSE)`- `r format(quarantine.in.101.b, scientific = FALSE)` individuals of body-weight `r bw_0` : `r quarantine.max`
* Nursery - divide `r format(nursery.in.101.a, scientific = FALSE)` - `r format(nursery.in.101.b, scientific = FALSE)`, `r quarantine.max`g, shrimp between `r nursery.101.division` independently operating system(s), raise to `r juvenile.max`g.
* Growout - rear `r format(growout.in.101.a, scientific = FALSE)` - `r format(growout.in.101.b, scientific = FALSE)`, `r juvenile.max`g, shrimp within `r growout.101.division.a` - `r growout.101.tank.multiplier` system(s), raise to `r growout.max`g.
* Depuration - purge up to `r format(depurate.in.primo, scientific = FALSE)`, `r growout.max`g shrimp - split between `r depurate.tanks.primo` tank(s), operated by `r depurate.primo.division` treatment system(s).

``` {r system_loading_101}

# build system loading onto production plan 101
system.loading.101 <- prod.plan.101 %>%
  mutate(total.number = case_when(system == "quarantine" ~ quarantine.in.101.a * exp(1)^(log(quarantine.survival) / quarantine.period.101 * batch_day),
                                  system == "nursery" ~ nursery.in.101.a * exp(1)^(log(nursery.survival) / nursery.period.101 * (batch_day - (quarantine.period.101 + 1))),
                                  system == "growout" ~ growout.in.101.a * exp(1)^(log(growout.survival) / growout.period.101 * (batch_day - (quarantine.period.101 + 1) - nursery.period.101)),
                                  system == "depurate" ~ depurate.in.101),
         total.number = case_when(system == "quarantine" & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ quarantine.in.101.b * exp(1)^(log(quarantine.survival) / quarantine.period.101 * batch_day), TRUE ~ total.number),
         total.number = case_when(system == "nursery" & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ nursery.in.101.b * exp(1)^(log(nursery.survival) / nursery.period.101 * (batch_day - (quarantine.period.101 + 1))), TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ growout.in.101.b * exp(1)^(log(growout.survival) / growout.period.101 * (batch_day - (quarantine.period.101 + 1) - nursery.period.101)), TRUE ~ total.number),
         total.number = case_when(system == "nursery" & batch_day >= shrimp.5.g ~ total.number - nursery.harvest.101 * nursery.101.division, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 ~ total.number - harvest.101.1 * growout.101.division.a, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 + 14 ~ total.number - harvest.101.2 * growout.101.division.a, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.harvest.day.32 + 28 ~ 0, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.32.g & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ total.number - harvest.101.1 * growout.101.division.b, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.32.g + 15 & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ total.number - harvest.101.2 * growout.101.division.b, TRUE ~ total.number),
         total.number = case_when(system == "growout" & batch_day >= shrimp.32.g + 30 & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ 0, TRUE ~ total.number),
         process.number = case_when(system == "quarantine" ~ total.number / quarantine.101.division,
                                    system == "nursery" ~ total.number / nursery.101.division,
                                    system == "growout" ~ total.number / growout.101.division.a,
                                    system == "depurate" ~ total.number / depurate.101.division),
         process.number = case_when(system == "growout" & batch %in% c("lag.batch.1", "lag.batch.3", "lag.batch.5", "lag.batch.7", "lag.batch.9", "lag.batch.11") ~ total.number / growout.101.tank.multiplier, TRUE ~ process.number),
         bw = case_when(system == "depurate" ~ 32, TRUE ~ (bw_0^c_1 + c_2 * batch_day)^c_4),
         feed.rate = case_when(system == "quarantine" ~ exp(quarantine.feed.twinlog$coef[1]) * bw ^ quarantine.feed.twinlog$coef[2],
                               system == "nursery" ~ exp(juvenile.nursery.feed.log$coef[1] + bw * juvenile.nursery.feed.log$coef[2]),
                               system == "growout" ~ growout.feed,
                               system == "depurate" ~ depurate.feed),
         protein.proportion = case_when(system == "quarantine" ~ quarantine.protein,
                                        system == "nursery" ~ nursery.protein,
                                        system == "growout" ~ growout.protein,
                                        system == "depurate" ~ depurate.protein),
         total.bw.kg = bw * total.number / 1000,
         total.feed.kg = total.bw.kg * feed.rate,
         total.protein = total.feed.kg * protein.proportion,
         process.bw.kg = bw * process.number / 1000,
         process.feed.kg = process.bw.kg * feed.rate,
         process.protein = process.feed.kg * protein.proportion)
```

```{r SystemIndividuals101, fig.cap = "Total number of individuals per phase (101^st^ st. 2024).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

batch.names <- c("lag.batch.0" = "Batch 1", "lag.batch.1" = "Batch 2")

system.n.101 <- system.loading.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1")) %>%
  ggplot(aes(batch_day, total.number, color = system)) +
  geom_line() +
  xlim(0, 210) +
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in Batch") + 
  theme_minimal()

system.n.101
```

``` {r ProcessIndividuals101, fig.cap = "Total number of individuals per system (101^st^ st. 2024).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

tank.n.101 <- system.loading.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1")) %>%
  ggplot(aes(batch_day, process.number, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "Number of Shrimp in System") + 
  theme_minimal()

tank.n.101
```

The following feeding models were developed to estimate system loading across the production cycle through the developmental phases:

``` {r FeedPlot, fig.cap = "Feeding model - overlaid on feed tables.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

feed.plot <- feed %>%
  ggplot(aes(wt, feed_pc, color = phase)) +
  geom_line()+
  stat_function(fun = function(x) exp(quarantine.feed.twinlog$coef[1]) * x ^ quarantine.feed.twinlog$coef[2],
                color = 'orange', xlim = c(0.007, 1.2), alpha = 0.4) +
  stat_function(fun = function(x) nursery.feed,
                color = "orange", xlim = c(1.2, 3.0), alpha = 0.4) +
  stat_function(fun = function(x) exp(juvenile.feed.log$coef[1] + x * juvenile.feed.log$coef[2]),
                color = 'orange', xlim = c(3.0, 10), alpha = 0.4) +
  stat_function(fun = function(x) growout.feed,
                color = "orange", xlim = c(10, 32), alpha = 0.4) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Shrimp bodyweight (g)", y = "Feed as proportion of bodyweight") + 
  theme_minimal()

feed.plot
```

## 95^th^ st. (2022) System Loading:

``` {r feed_loading_95}

# get max loading for each system (overlapping batches where appropriate)
avg.loading.95 <- system.loading %>%
  group_by(system, facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get a summary table for all minus quarantine
facility.loading.95 <- system.loading %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum))
```

### Feed and protein maximum and average facility loading rates.

``` {r FeedLoadingTable95, ft.align="center"}

facility.loading.95 %>%
  flextable() %>%
  set_header_labels(n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"),  " st. 2022 facility loading rates (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab", bkm = "tab1"))
```

### Feed and protein maximum and average loading rates per day per system.

``` {r feed_loading_unit95}

# get max loading for individual system processes - filter one batch
process.loading_95 <- system.loading %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(n_max = max(process.number),
            feed.avg = mean(process.feed.kg),
            feed.max = max(process.feed.kg),
            protein.avg = mean(process.protein),
           protein.max = max(process.protein)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))
```

``` {r SystemFeedLoadingTable95, ft.align="center"}

process.loading_95 %>%
  flextable() %>%
  set_header_labels(system = "System",  n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
  set_caption(caption = as_paragraph("95", as_sup("th"),  " st. 2022 System loading rates."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))

```

## 95^th^ st. (2023) Facility Loading:

``` {r feed_loading_primo}

# get max loading for each system in primo (overlapping batches where appropriate)
avg.loading.primo <- system.loading.primo %>%
  group_by(system, facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "growout", "depurate")))

# ignore the above and get a summary table for all minus quarantine
facility.loading.primo <- system.loading.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum))
```

### Feed and protein maximum and average loading rates per day per system (phase).

``` {r FeedLoadingTablePrimo, ft.align="center"}

facility.loading.primo %>%
  flextable() %>%
  set_header_labels(n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"),  " st. 2023 facility loading rate (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### Feed and protein maximum and average loading rates per day per system.

``` {r feed_loading_unit_primo}

# get max loading for individual system processes - filter one batch
process.loading_primo <- system.loading.primo %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(n_max = max(process.number),
            feed.avg = mean(process.feed.kg),
            feed.max = max(process.feed.kg),
            protein.avg = mean(process.protein),
            protein.max = max(process.protein)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "growout", "depurate")))
```

``` {r SystemFeedLoadingTablePrimo, ft.align="center"}

process.loading_primo %>%
  flextable() %>%
  set_header_labels(system = "System",  n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
  set_caption(caption = as_paragraph("95", as_sup("th"),  " st. 2023 System loading rates."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

## 101^st^ st. (2024) Facility Loading:

``` {r feed_loading_101}

# get max loading for each system in primo (overlapping batches where appropriate)
avg.loading.101 <- system.loading.101 %>%
  group_by(system, facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "growout", "depurate")))

# ignore the above and get a summary table for all minus quarantine
facility.loading.101 <- system.loading.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(n_sum = sum(total.number),
            feed.sum = sum(total.feed.kg),
            protein.sum = sum(total.protein)) %>%
  summarise(n_max = max(n_sum),
            feed.avg = mean(feed.sum),
            feed.max = max(feed.sum),
            protein.avg = mean(protein.sum),
            protein.max = max(protein.sum))
```

### Feed and protein maximum and average loading rates per day per system (phase).

``` {r FeedLoadingTable101, ft.align="center"}

facility.loading.101 %>%
  flextable() %>%
  set_header_labels(n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 facility loading rates (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### Feed and protein maximum and average loading rates per system.

``` {r feed_loading_101a_unit}

# get max loading for individual system processes - filter one batch
process.loading_101.a <- system.loading.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(n_max = max(process.number),
            feed.avg = mean(process.feed.kg),
            feed.max = max(process.feed.kg),
            protein.avg = mean(process.protein),
            protein.max = max(process.protein)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "growout", "depurate")))
```

``` {r SystemFeedLoadingTable101a, ft.align="center"}

process.loading_101.a %>%
  flextable() %>%
  set_header_labels(system = "System",  n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
  set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 system loading rates (four raceway strategy)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r feed_loading_101b_unit}

# get max loading for individual system processes - filter one batch
process.loading_101.b <- system.loading.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(n_max = max(process.number),
            feed.avg = mean(process.feed.kg),
            feed.max = max(process.feed.kg),
            protein.avg = mean(process.protein),
            protein.max = max(process.protein)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "growout", "depurate")))
```

``` {r SystemFeedLoadingTable101b, ft.align="center"}

process.loading_101.b %>%
  flextable() %>%
  set_header_labels(system = "System",  n_max = "Max n", feed.avg = "Feed avg (Kg/day)", feed.max = "Feed max (Kg/day)", protein.avg = "Protein avg (Kg/day)", protein.max = "Protein max (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
  set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 system loading rates (six raceway strategy)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

***

# Water Quality Defining Parameters

Based on feed inputs, the following parameters (inputs or requirements) can be modelled:

* TAN--N Total ammonia nitrogen produced (ionised ammonia + un-ionised ammonia NH~4~^+^--N + NH~3~--N)
* TSS Total suspended solids produced
* CO~2~ Carbon dioxide produced
* O~2~D Oxygen demand
* Alk Alkalinity demand
* Carb Carbohydrate demand

``` {r loading_parameters_95}

# 95 st 2022 loading parameters
# for marine shrimp in zero-exchange system, Ptan = F * PC * 0.144
# for starvation, TAN =  0.067 mg N-NH3 / h / g
# starvation oxygen consumption ~ 1 mg Oxy/g/h
# carb calculations: TAN * 15.17 is carb requirement, less feed carb content feed * 0.1089 / 0.4
system.parameters.95 <- system.loading %>%
  mutate(total.tan = case_when(system == "depurate" ~ total.bw.kg * 0.067 * 24 / 1000,
                               TRUE ~ total.feed.kg * protein.proportion * 0.144), # total tan in kg
         process.tan = case_when(system == "depurate" ~ process.bw.kg * 0.067 * 24 / 1000,
                                 TRUE ~ process.feed.kg * protein.proportion * 0.144),
         total.tss.clearwater = total.feed.kg * 0.25,
         process.tss.clearwater = process.feed.kg * 0.25,
         total.tss = case_when(system == "quarantine" ~ total.feed.kg * 0.25,
                               system == "depurate" ~ total.tan * 0.2,
                               TRUE ~ (total.feed.kg * 0.25) + (total.tan * 8.07)),
         process.tss = case_when(system == "quarantine" ~ process.feed.kg * 0.25,
                                 system == "depurate" ~ process.tan * 0.2,
                                 TRUE ~ (process.feed.kg * 0.25) + (process.tan * 8.07)),
         total.od = case_when(system == "quarantine" ~ total.feed.kg * 0.25 + total.tan * 4.57,
                              system == "depurate" ~ total.bw.kg * 1 / 1000 * 24,
                              TRUE ~ (total.feed.kg * 0.25) + (total.tan * 4.71)),
         process.od = case_when(system == "quarantine" ~ process.feed.kg * 0.25 + process.tan * 4.57,
                                system == "depurate" ~ process.bw.kg * 1 / 1000 * 24,
                                TRUE ~ (process.feed.kg * 0.25) + (process.tan * 4.71)),
         total.alk = case_when(system == "quarantine" | system == "depurate" ~ total.tan * 7.05,
                               TRUE ~ total.tan * 3.57), # 3.57 g of alkalinity consumed in heterotrophic systems
         process.alk = case_when(system == "quarantine" | system == "depurate" ~ process.tan * 7.05,
                                 TRUE ~ process.tan * 3.57),
         total.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                TRUE ~ total.feed.kg * protein.proportion * 0.144 * 15.17 - (total.feed.kg * 0.1089 / 0.4)),
         process.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                  TRUE ~ process.feed.kg * protein.proportion * 0.144 * 15.17 - (process.feed.kg * 0.1089 / 0.4)),
         total.co2 =  total.od * 1.375,
         process.co2 = process.od * 1.375)
```

``` {r loading_parameters_primo}

# 95 st 2023 loading parameters
# for marine shrimp in zero-exchange system, Ptan = F * PC * 0.144
system.parameters.primo <- system.loading.primo %>%
  mutate(total.tan = case_when(system == "depurate" ~ total.bw.kg * 0.067 * 24 / 1000,
                               TRUE ~ total.feed.kg * protein.proportion * 0.144), # total tan in kg
         process.tan = case_when(system == "depurate" ~ process.bw.kg * 0.067 * 24 / 1000,
                                 TRUE ~ process.feed.kg * protein.proportion * 0.144),
         total.tss.clearwater = total.feed.kg * 0.25,
         process.tss.clearwater = process.feed.kg * 0.25, 
         total.tss = case_when(system == "quarantine" ~ total.feed.kg * 0.25,
                               system == "depurate" ~ total.tan * 0.2,
                               TRUE ~ (total.feed.kg * 0.25) + (total.tan * 8.07)),
         process.tss = case_when(system == "quarantine" ~ process.feed.kg * 0.25,
                                 system == "depurate" ~ process.tan * 0.2,
                                 TRUE ~ (process.feed.kg * 0.25) + (process.tan * 8.07)),
         total.od = case_when(system == "quarantine" ~ total.feed.kg * 0.25 + total.tan * 4.57,
                              system == "depurate" ~ total.bw.kg * 1 / 1000 * 24,
                              TRUE ~ (total.feed.kg * 0.25) + (total.tan * 4.71)),
         process.od = case_when(system == "quarantine" ~ process.feed.kg * 0.25 + process.tan * 4.57,
                                system == "depurate" ~ process.bw.kg * 1 / 1000 * 24,
                                TRUE ~ (process.feed.kg * 0.25) + (process.tan * 4.71)),
         total.alk = case_when(system == "quarantine" | system == "depurate" ~ total.tan * 7.05,
                               TRUE ~ total.tan * 3.57), # 3.57 g of alkalinity consumed in heterotrophic systems
         process.alk = case_when(system == "quarantine" | system == "depurate" ~ process.tan * 7.05,
                                 TRUE ~ process.tan * 3.57),
         total.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                TRUE ~ total.feed.kg * protein.proportion * 0.144 * 15.17 - (total.feed.kg * 0.1089 / 0.4)),
         process.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                  TRUE ~ process.feed.kg * protein.proportion * 0.144 * 15.17 - (process.feed.kg * 0.1089 / 0.4)),
         total.co2 =  total.od * 1.375,
         process.co2 = process.od * 1.375)
```

``` {r loading_parameters_101}

# 101 st 2024 loading parameters
# for marine shrimp in zero-exchange system, Ptan = F * PC * 0.144
system.parameters.101 <- system.loading.101 %>%
  mutate(total.tan = case_when(system == "depurate" ~ total.bw.kg * 0.067 * 24 / 1000,
                               TRUE ~ total.feed.kg * protein.proportion * 0.144), # total tan in kg
         process.tan = case_when(system == "depurate" ~ process.bw.kg * 0.067 * 24 / 1000,
                                 TRUE ~ process.feed.kg * protein.proportion * 0.144),
         total.tss.clearwater = total.feed.kg * 0.25,
         process.tss.clearwater = process.feed.kg * 0.25, 
         total.tss = case_when(system == "quarantine" ~ total.feed.kg * 0.25,
                               system == "depurate" ~ total.tan * 0.2,
                               TRUE ~ (total.feed.kg * 0.25) + (total.tan * 8.07)),
         process.tss = case_when(system == "quarantine" ~ process.feed.kg * 0.25,
                                 system == "depurate" ~ process.tan * 0.2,
                                 TRUE ~ (process.feed.kg * 0.25) + (process.tan * 8.07)),
         total.od = case_when(system == "quarantine" ~ total.feed.kg * 0.25 + total.tan * 4.57,
                              system == "depurate" ~ total.bw.kg * 1 / 1000 * 24,
                              TRUE ~ (total.feed.kg * 0.25) + (total.tan * 4.71)),
         process.od = case_when(system == "quarantine" ~ process.feed.kg * 0.25 + process.tan * 4.57,
                                system == "depurate" ~ process.bw.kg * 1 / 1000 * 24,
                                TRUE ~ (process.feed.kg * 0.25) + (process.tan * 4.71)),
         total.alk = case_when(system == "quarantine" | system == "depurate" ~ total.tan * 7.05,
                               TRUE ~ total.tan * 3.57), # 3.57 g of alkalinity consumed in heterotrophic systems
         process.alk = case_when(system == "quarantine" | system == "depurate" ~ process.tan * 7.05,
                                 TRUE ~ process.tan * 3.57),
         total.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                TRUE ~ total.feed.kg * protein.proportion * 0.144 * 15.17 - (total.feed.kg * 0.1089 / 0.4)),
         process.carb = case_when(system == "quarantine" | system == "depurate" ~ 0,
                                  TRUE ~ process.feed.kg * protein.proportion * 0.144 * 15.17 - (process.feed.kg * 0.1089 / 0.4)),
         total.co2 =  total.od * 1.375,
         process.co2 = process.od * 1.375)
```

``` {r mass_balance_parameters}

# define water quality parameters
desired.tss <- 250 #  250 mg/l in tanks as a starting point
desired.tss.cw <- 20
desired.o2 <- 5.0 # min 5 mg/l in tanks
desired.tan <- 1 # max 1 mg/l TAN in tanks
desired.nitrate <- 50 # max 50 mg/l nitrate in tanks
desired.co2 <- 15 # max 15 mg/l in tanks
desired.t <- 30 # system operating temp in C
site.altitude <- 10 # site altitude in metres
cone.bar <- 0.7
feeding.period <- 24
metabolic.period <- case_when(feeding.period < 20 ~ feeding.period + 4, TRUE ~ 24)

# constants
k <- 1.42903
beta.oxygen <- exp(-58.3877 + 85.8079 *  (100/(desired.t + 273.15)) + 23.8439 * log((desired.t+273.15) / 100))
barometric.pressure <- 10^(2.88014 - site.altitude/19748.2)
water.v.pressure <- 4.7603 * exp(0.0645 * desired.t)
oxygen.percent <- 20.95
oxygen.saturation <- 1000 * k * beta.oxygen * oxygen.percent / 100 * ((barometric.pressure - water.v.pressure) / 760) # if cone used at pressure swap out barometric.pressure for cone.pressure
cone.pressure <- cone.bar * 750.06 + barometric.pressure
oxygen.saturation.saline <- oxygen.saturation * 0.8
```

``` {r mass_balance_equations}

# component specifics
# system efficiency 
tan.c1 <- desired.tan
tan.cbest <- 0
tan.te <- 0.9
tan.c2 <- tan.c1 + tan.te * (tan.cbest - tan.c1)

co2.c1 <- desired.co2
co2.cbest <- 0.5
co2.te <- 0.7
co2.c2 <- co2.c1 + co2.te * (co2.cbest - co2.c1)

tss.c1 <- desired.tss
tss.cbest <- 0
tss.te <- 0.21
tss.c2 <- tss.c1 + tss.te * (tss.cbest - tss.c1)

oxy.c1 <- desired.o2 # min 5 mg/l in tanks
oxy.cbest <- oxygen.saturation.saline
oxy.te <- 0.99
oxy.c2 <- oxy.c1 + oxy.te * (oxy.cbest - oxy.c1)

tss.c1.cw <- desired.tss.cw
tss.cbest.cw <- 0
tss.te.cw <- 0.7
tss.c2.cw <- tss.c1.cw + tss.te.cw * (tss.cbest.cw - tss.c1.cw)
```

***

## Nitrogen Management

TAN--N loading

### 95^th^ st. 2022 TAN--N summary

``` {r tan_summary_95}

# get max tan loading for each system 95th st 2022 (overlapping batches where appropriate)
tan.system.95 <- system.parameters.95 %>%
  group_by(system, facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading minus quarantine
facility.system.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum))

# get max tan loading for individual system processes 95th st 2022
tan.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(tan.p.max = max(process.tan),
            tan.p.avg = mean(process.tan)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join tan summary tibbles 95th st 2022
tan.summary.95 <- left_join(tan.system.95, tan.process.95, by = "system")
```

``` {r FacilityTanLoadingTable95, ft.align="center"}

facility.system.95 %>%
  flextable() %>%
  set_header_labels(tan.s.max = "Max TAN (Kg/day)", tan.s.avg = "Avg TAN (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility loading rates (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TanLoadingTable95, ft.align="center"}

tan.process.95 %>%
  flextable() %>%
  set_header_labels(system = "System", tan.p.max = "Max TAN (Kg/day)", tan.p.avg = "Avg TAN (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System loading rates."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))

```

``` {r TanProfile95, fig.cap = "95^th^ st. 2022 System TAN--N profile.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot tan loading across batch run 95th st 2022
tank.tan.95 <- system.parameters.95 %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.tan, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = "TAN--N (kg)") + 
  theme_minimal()

tank.tan.95
```

### 95^th^ st. 2023 TAN--N summary

``` {r tan_summary_primo}

# get max tan loading for each system 95th st 2023 (overlapping batches where appropriate)
tan.system.primo <- system.parameters.primo %>%
  group_by(system, facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading minus quarantine
facility.system.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum))

# get max tan loading for individual system processes 95th st 2023
tan.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(tan.p.max = max(process.tan),
            tan.p.avg = mean(process.tan)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join tan summary tibbles 95th st 2023
tan.summary.primo <- left_join(tan.system.primo, tan.process.primo, by = "system")
```

``` {r FacilityTanLoadingTablePrimo, ft.align="center"}

facility.system.primo %>%
  flextable() %>%
  set_header_labels(tan.s.max = "Max TAN (Kg/day)", tan.s.avg = "Avg TAN (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Facility loading rates (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TanLoadingTablePrimo, ft.align="center"}

tan.process.primo %>%
  flextable() %>%
  set_header_labels(system = "System", tan.p.max = "Max TAN (Kg/day)", tan.p.avg = "Avg TAN (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System loading rates."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TanProfilePrimo, fig.cap = "95^th^ st. 2023 System TAN--N profile.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot tan loading across batch run 95th st 2023
tank.tan.primo <- system.parameters.primo %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.tan, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "TAN--N (kg)") + 
  theme_minimal()

tank.tan.primo
```

### 101^st^ st. 2024 TAN--N summary

``` {r tan_summary_101}

# get max tan loading for each system 101th st 2024 (overlapping batches where appropriate)
tan.system.101 <- system.parameters.101 %>%
  group_by(system, facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading minus quarantine
facility.system.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tan.sum = sum(total.tan)) %>%
  summarise(tan.s.max = max(tan.sum),
            tan.s.avg = mean(tan.sum))

# get max tan loading for individual system processes 101st st 2024 4 raceway batch
tan.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(tan.p.max.a = max(process.tan),
            tan.p.avg.a = mean(process.tan)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max tan loading for individual system processes 101st st 2024 6 raceway batch
tan.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(tan.p.max.b = max(process.tan),
            tan.p.avg.b = mean(process.tan)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join tan summary tibbles 101st st 2024
tan.summary.101 <- left_join(tan.process.101a, tan.process.101b, by = "system")
```

``` {r FacilityTanLoadingTable101, ft.align = "center"}

facility.system.101 %>%
  flextable() %>%
  set_header_labels(tan.s.max = "Max TAN (Kg/day)", tan.s.avg = "Avg TAN (Kg/day)") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility loading rates (overlapping batches where appropriate)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TanLoadingTable101, ft.align = "center"}

tan.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", tan.p.max.a = "System max TAN A", tan.p.avg.a = "System avg TAN A", tan.p.max.b = "System max TAN B", tan.p.avg.b = "System avg TAN B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System loading rates."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TanProfile101, fig.cap = "101^st^ st. 2024 System TAN--N profile.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot tan loading across batch run 101st st 2024
tank.tan.101 <- system.parameters.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1")) %>%
  ggplot(aes(facility_day, process.tan, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Growout", "Depurate")) +
  labs(x = "Day", y = "TAN--N (kg)") + 
  theme_minimal()

tank.tan.101
```

Ammonia removal from intensive aquaculture production can be managed by three distinct pathways:

* Photoautotrophic (algal)
* Autotrophic (bacterial)
* Heterotrophic (bacterial)

Of relevance in the production process at SyAqua Americas are autotrophic (quarantine and depuration/ purging) and heterotrophic (nursery, juvenile and grow-out) pathways.

Chemoautotrophic pathway (simplified) NH~4~^+^ + O~2~ + alkalinity &rarr; NO~2~^-^ &rarr; NO~3~^-^ + CO~2~ + small amount of bacterial biomass

Heterotrophic pathway (simplified) NH~4~^+^ + O~2~ + alkalinity + organic C &rarr; large amount of bacterial biomass + CO~2~

The carbon/ nitrogen ratio influences the relative proportion of autotrophic/ heterotrophic bacterial community and therefore may be used as a management tool for determination of nitrogen removal pathway.

Stoichiometric equations predict that for every g of ammonia-nitrogen converted to microbial biomass (by heterotrophic bacteria), 15.17 g of carbohydrates or 6.07 g of organic carbon is consumed. Organic carbon can be made available from livestock feed constituents and supplementary carbohydrate additions e.g. molasses or other source.

NH~4~^+^ -- N within the quarantine systems would typically be removed primarily by the chemoautotrophic pathway, utilising a fixed film moving-bed bioreactor. The volume of the biomedia would be dictated by the surface area and the maximum potential daily NH~4~^+^ -- N loading. 

Suggested minimum quarantine biomedia surface areas are as follows (based on a 24 hr metabolic period):

95^th^ st. 2022; `r format(tan.summary.95[1,2] / (0.4 / 1000), digits = 3)`m^2^  
95^th^ st. 2023; `r format(tan.summary.primo[1,2] / (0.4 / 1000), digits = 3)`m^2^  
101^st^ st. 2024; `r format(tan.summary.101[1,2] / (0.4 / 1000), digits = 3)`m^2^

NH~4~^+^ -- N within the depuration/ purging systems would typically be managed by water exchange and minimal nitrification/ ammonia sequestration from bacteria present in the sand filter/ water column.

The charts below indicate theoretical carbohydrate additions required to supplement organic carbon supplied in feed (nursery/ juvenile/ grow-out stages only). 

Calculations based upon:

TAN produced * bacterial carbohydrate demand - carbohydrate in feed

Feed input * protein proportion * 0.144 * 15.17 - (feed input * 0.1089 / 0.4)

### 95^th^ st. 2022

``` {r CarbProfile95, fig.cap = "95^th^ st. 2022 Theoretical supplimentary carbohydrate requirement (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot carb requirement across batch run 95th st 2022
tank.carb.95 <- system.parameters.95 %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, process.carb, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("nursery", "juvenile", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Juvenile", "Growout")) +
  labs(x = "Day", y = "Supplimentary carb (Kg/day)") + 
  theme_minimal()

tank.carb.95
```

### 95^th^ st. 2023

``` {r CarbProfilePrimo, fig.cap = "95^th^ st. 2023 Theoretical supplimentary carbohydrate requirement (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot carb requirement across batch run 95th st 2023
tank.carb.primo <- system.parameters.primo %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, process.carb, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("nursery", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Growout")) +
  labs(x = "Day", y = "Supplimentary carb (Kg/day)") + 
  theme_minimal()

tank.carb.primo
```

### 101^st^ st. 2024

``` {r CarbProfile101, fig.cap = "101^st^ st. 2024 Theoretical supplimentary carbohydrate requirement (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot tan loading across batch run 101st st 2024
tank.carb.101 <- system.parameters.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1") & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(facility_day, process.carb, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("nursery", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Growout")) +
  labs(x = "Day", y = "Supplimentary carb (Kg/day)") + 
  theme_minimal()

tank.carb.101
```

***

## Solids Management

Solids within the production process will be comprised of uneaten feed, faeces and bacterial biomass.

The literature indicates a total suspended solids (TSS) concentration of 200-300 mg/l is typical within biofloc operation, and levels of up to 500 mg/l may be acceptable without reduction of welfare or growth of shrimp. 

Solids concentration will increase in zero exchange systems and active management techniques may be required to maintain optimal levels of TSS.

TSS accumulation can be modelled according to system management based on feed input for chemoautotrophic-managed nitrogen pathways or feed input and bacterial biomass synthesised for heterotrophic-managed nitrogen pathways.

Solids profile not currently awailable from SyAqua.   
Generic biofloc solids profile as follows: < 48 $\mu$m 53%, 48-100 $\mu$m 12%, > 100 $\mu$m 36%  
Generic clearwater RAS solids profile (trout): < 40 $\mu$m 10%, 40-100 $\mu$m 40%, > 100 $\mu$m 50%

Settling velocities (caveat - estimated specific gravity 1.05):
48 $\mu$ `r (9.81 * (48e-6)^2 * (1050 - 1000)) / (18 * 0.851e-3)` m/s
75 $\mu$ `r (9.81 * (75e-6)^2 * (1050 - 1000)) / (18 * 0.851e-3)` m/s
100 $\mu$ `r (9.81 * (100e-6)^2 * (1050 - 1000)) / (18 * 0.851e-3)` m/s



### 95^th^ st. 2022

``` {r solids_summary_95}

# get max tss loading for each system 95th st 2022 (overlapping batches where appropriate)
tss.system.95 <- system.parameters.95 %>%
  group_by(system, facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading
tss.facility.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))

# get max tss loading for individual system processes 95th st 2022
tss.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(tss.p.max = max(process.tss),
            tss.p.avg = mean(process.tss)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# perform clearwater calcs for comparison
tss.facility.clearwater.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss.clearwater)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))

tss.process.clearwater.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(tss.p.max = max(process.tss.clearwater),
            tss.p.avg = mean(process.tss.clearwater)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join facility tables
tss.facility.summary.95 <-
  bind_cols(tss.facility.clearwater.95, tss.facility.95)

tss.process.summary.95 <-
  left_join(tss.process.clearwater.95, tss.process.95, by = "system")

# join tss summary tibbles 95th st 2022
tss.summary.95 <- left_join(tss.system.95, tss.process.95, by = "system")
```

``` {r FacilityTssLoadingTable95, ft.align = "center"}

tss.facility.summary.95 %>%
  flextable() %>%
  set_header_labels(tss.s.max...1 = "Max TSS CW", tss.s.avg...2 = "Avg TSS CW ", tss.s.max...3 = "Max TSS BF", tss.s.avg...4 = "Avg TSS BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility loading rates (Kg/day TSS modelled for clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TssLoadingTable95, ft.align = "center"}

tss.process.summary.95 %>%
  flextable() %>%
  set_header_labels(system = "System", tss.p.max.x = "Max TSS CW", tss.p.avg.x = "Avg TSS CW", tss.p.max.y = "Max TSS BF", tss.p.avg.y = "Avg TSS BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System loading rates (Kg/day TSS modelled for clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 95^th^ st. 2023

``` {r solids_summary_primo}

# get max tss loading for each system 95th st 2023 (overlapping batches where appropriate)
tss.system.primo <- system.parameters.primo %>%
  group_by(system, facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading
tss.facility.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))

# get max tss loading for individual system processes 95th st 2023
tss.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(tss.p.max = max(process.tss),
            tss.p.avg = mean(process.tss)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# perform clearwater calcs for comparison
tss.facility.clearwater.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss.clearwater)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))

tss.process.clearwater.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(tss.p.max = max(process.tss.clearwater),
            tss.p.avg = mean(process.tss.clearwater)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join facility tables
tss.facility.summary.primo <-
  bind_cols(tss.facility.clearwater.primo, tss.facility.primo)

tss.process.summary.primo <-
  left_join(tss.process.clearwater.primo, tss.process.primo, by = "system")

# join tss summary tibbles 95th st 2023
tss.summary.primo <- left_join(tss.system.primo, tss.process.primo, by = "system")
```

``` {r FacilityTssLoadingTablePrimo, ft.align = "center"}

tss.facility.summary.primo %>%
  flextable() %>%
  set_header_labels(tss.s.max...1 = "Max TSS CW", tss.s.avg...2 = "Avg TSS CW ", tss.s.max...3 = "Max TSS BF", tss.s.avg...4 = "Avg TSS BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Facility loading rates (Kg/day TSS modelled for clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TssLoadingTable_Primo, ft.align = "center"}

tss.process.summary.primo %>%
  flextable() %>%
  set_header_labels(system = "System", tss.p.max.x = "Max TSS CW", tss.p.avg.x = "Avg TSS CW", tss.p.max.y = "Max TSS BF", tss.p.avg.y = "Avg TSS BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System loading rates (Kg/day TSS modelled for clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 101^st^ st. 2024

``` {r solids_summary_101}

# get max tss loading for each system 101th st 2024 (overlapping batches where appropriate)
tss.system.101 <- system.parameters.101 %>%
  group_by(system, facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility loading
tss.facility.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))

# get max tss loading for individual system processes 101st st 2024 4 raceway batch
tss.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(tss.p.max.a = max(process.tss),
            tss.p.avg.a = mean(process.tss)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max tss loading for individual system processes 101st st 2024 6 raceway batch
tss.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(tss.p.max.b = max(process.tss),
            tss.p.avg.b = mean(process.tss)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join tss summary tibbles 101st st 2024
tss.summary.101 <- left_join(tss.process.101a, tss.process.101b, by = "system")

# perform clearwater calcs for comparison
tss.facility.clearwater.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(tss.sum = sum(total.tss.clearwater)) %>%
  summarise(tss.s.max = max(tss.sum),
            tss.s.avg = mean(tss.sum))


# get max tss loading for individual system processes 101st st 2024 4 raceway batch
tss.process.clearwater.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(tss.p.max.a = max(process.tss.clearwater),
            tss.p.avg.a = mean(process.tss.clearwater)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max tss loading for individual system processes 101st st 2024 4 raceway batch
tss.process.clearwater.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(tss.p.max.b = max(process.tss.clearwater),
            tss.p.avg.b = mean(process.tss.clearwater)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join facility tables
tss.facility.summary.101 <-
  bind_cols(tss.facility.clearwater.101, tss.facility.101)

tss.process.summary.cw.101 <-
  left_join(tss.process.clearwater.101a, tss.process.clearwater.101b, by = "system")
```

``` {r FacilityTssLoadingTable101, ft.align = "center"}

tss.facility.summary.101 %>%
  flextable() %>%
  set_header_labels(tss.s.max...1 = "Max TSS CW", tss.s.avg...2 = "Avg TSS CW ", tss.s.max...3 = "Max TSS BF", tss.s.avg...4 = "Avg TSS BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility loading rates (Kg/day TSS modelled for clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TssLoadingTableCW101, ft.align = "center"}

tss.process.summary.cw.101 %>%
  flextable() %>%
  set_header_labels(system = "System", tss.p.max.a = "System max TSS A", tss.p.avg.a = "System avg TSS A", tss.p.max.b = "System max TSS B", tss.p.avg.b = "System avg TSS B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System loading rates (Kg/day modelled for clearwater operation)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r TssLoadingTableBF101, ft.align = "center"}

tss.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", tss.p.max.a = "System max TSS A", tss.p.avg.a = "System avg TSS A", tss.p.max.b = "System max TSS B", tss.p.avg.b = "System avg TSS B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System loading rates (Kg/day modelled for biofloc operation)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

A cumulative TSS sum may give an indication of the timing within the production run that the desired TSS will be achieved. From this point onwards, solids will require either continuous or periodic removal to maintain TSS within acceptable limits.

Calculations based upon full tanks:

``` {r tank_volumes}

# tank volumes
nursery.tank <- 15
raceway.tank <- 80
raceway.tank.101 <- 60
purging.unit <- 5 * 4
packing.volume <- 15.6
```

* Nursery `r format(nursery.tank, scientific = FALSE)` m^3^
* Juvenile (95^th^ 2022) `r format(raceway.tank, scientific = FALSE)` m^3^
* Growout `r format(raceway.tank, scientific = FALSE)` m^3^

### 95^th^ st. 2022

``` {r tss_cumsum_95}

# get cumulative sum grouped by system 95th st 2022
cumulative.tss.95 <- system.parameters.95 %>%
  group_by(system, batch) %>%
  mutate(cs = cumsum(process.tss),
         cumulative.tss = case_when(system == "juvenile"  ~ cs * 1e6 / (1000 * raceway.tank),
                                    system == "growout" ~ cs * 1e6 / (1000 * raceway.tank),
                                    system == "nursery" ~ cs * 1e6 / (1000 * nursery.tank),
                                    TRUE ~ 0),
         total.drum.flow = abs(total.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         process.drum.flow = abs(process.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         total.drum.flow.cw = abs(total.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         process.drum.flow.cw = abs(process.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         total.drum.water.use.cw = total.feed.kg * 200 / 1000,
         process.drum.water.use.cw = process.feed.kg * 200 / 1000,
         total.drum.water.use.bf = case_when(system == "nursery" | system == "juvenile" | system == "growout" ~ total.tss / total.tss.clearwater * total.feed.kg * 50 / 1000, TRUE ~ 0),
         process.drum.water.use.bf = process.tss / process.tss.clearwater * process.feed.kg * 50 / 1000)
```

``` {r TssCumplot95, fig.cap = "95^th^ st. 2022 Cumulative TSS accumulation - without solids management (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot cumulative tss loading across batch run 95th st 2022
tss.cumplot.95 <- cumulative.tss.95 %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, cumulative.tss, color = system)) +
  geom_line()+
  geom_hline(yintercept=250, linetype="dashed", color = "darkgrey") + 
  scale_color_manual("", breaks = c("nursery", "juvenile", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Juvenile", "Growout")) +
  labs(x = "Day", y = "Cumulative TSS (mg/l)") + 
  theme_minimal()

tss.cumplot.95
```

### 95^th^ st. 2023

``` {r tss_cumsum_primo}

# get cumulative sum grouped by system 95th st 2023
cumulative.tss.primo <- system.parameters.primo %>%
  group_by(system, batch) %>%
  mutate(cs = cumsum(process.tss),
         cumulative.tss = case_when(system == "growout" ~ cs * 1e6 / (1000 * raceway.tank),
                                    system == "nursery" ~ cs * 1e6 / (1000 * raceway.tank),
                                    TRUE ~ 0),
         total.drum.flow = abs(total.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         process.drum.flow = abs(process.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         total.drum.flow.cw = abs(total.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         process.drum.flow.cw = abs(process.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         total.drum.water.use.cw = total.feed.kg * 200 / 1000,
         process.drum.water.use.cw = process.feed.kg * 200 / 1000,
         total.drum.water.use.bf = total.tss / total.tss.clearwater * total.feed.kg * 50 / 1000,
         process.drum.water.use.bf = process.tss / process.tss.clearwater * process.feed.kg * 50 / 1000)
```

``` {r TssCumplotPrimo, fig.cap = "95^th^ st. 2023 Cumulative TSS accumulation - without solids management (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot cumulative tss loading across batch run 95th st 2023
tss.cumplot.primo <- cumulative.tss.primo %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, cumulative.tss, color = system)) +
  geom_line()+
  geom_hline(yintercept=250, linetype="dashed", color = "darkgrey") +
  scale_color_manual("", breaks = c("nursery", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Growout")) +
  labs(x = "Day", y = "Cumulative TSS (mg/l)") + 
  theme_minimal()

tss.cumplot.primo
```

### 101^st^ st. 2024

``` {r tss_cumsum_101}

# get cumulative sum grouped by system 101st st 2024
cumulative.tss.101 <- system.parameters.101 %>%
  group_by(system, batch) %>%
  mutate(cs = cumsum(process.tss),
         cumulative.tss = case_when(system == "growout" ~ cs * 1e6 / (1000 * raceway.tank.101),
                                    system == "nursery" ~ cs * 1e6 / (1000 * raceway.tank.101),
                                    TRUE ~ 0),
         total.drum.flow = abs(total.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         process.drum.flow = abs(process.tss * 1e6 / (tss.c2 - tss.c1) / 24 / 1000),
         total.drum.flow.cw = abs(total.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         process.drum.flow.cw = abs(process.tss.clearwater * 1e6 / (tss.c2.cw - tss.c1.cw) / 24 / 1000),
         total.drum.water.use.cw = total.feed.kg * 200 / 1000,
         process.drum.water.use.cw = process.feed.kg * 200 / 1000,
         total.drum.water.use.bf = total.tss / total.tss.clearwater * total.feed.kg * 50 / 1000,
         process.drum.water.use.bf = process.tss / process.tss.clearwater * process.feed.kg * 50 / 1000)
```

``` {r TssCumplot101, fig.cap = "101^st^ st. 2024 Cumulative TSS accumulation - without solids management (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot cumulative tss loading across batch run 101st st 2024
tss.cumplot.101 <- cumulative.tss.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1") & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(facility_day, cumulative.tss, color = system)) +
  geom_line()+
  geom_hline(yintercept=250, linetype="dashed", color = "darkgrey") +
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("nursery", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Growout")) +
  labs(x = "Day", y = "Cumulative TSS (mg/l)") + 
  theme_minimal()

tss.cumplot.101
```

Drum Filter Flow Requirements/ or other solids removal device operating at `r tss.te * 100`% efficiency:

### 95^th^ st. 2022.

``` {r DrumFlowplot95, fig.cap = "95^th^ st. 2022 Drum filter flow requirements to maintain 250 mg/l TSS (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot drum filter flow requirement 95th 2022
drum.flowplot.95 <- cumulative.tss.95 %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, process.drum.flow, color = system)) +
  geom_line()+ 
  scale_color_manual("", breaks = c("nursery", "juvenile", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Juvenile", "Growout")) +
  labs(x = "Day", y = expression(paste("Drum Filter ", (m^3/hr)))) + 
  theme_minimal()

drum.flowplot.95
```

### 95^th^ st. 2023.

``` {r DrumFlowplotPrimo, fig.cap = "95^th^ st. 2023 Drum filter flow requirements to maintain 250 mg/l TSS (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot drum filter flow requirement 95th 2023
drum.flowplot.primo <- cumulative.tss.primo %>%
  filter(batch == "lag.batch.0" & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(batch_day, process.drum.flow, color = system)) +
  geom_line()+ 
  scale_color_manual("", breaks = c("nursery", "juvenile", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Juvenile", "Growout")) +
  labs(x = "Day", y = expression(paste("Drum Filter ", (m^3/hr)))) + 
  theme_minimal()

drum.flowplot.primo
```

### 101^st^ st. 2024.

``` {r DrumFlowplot101, fig.cap = "101^st^ st. 2024 Drum filter flow requirements to maintain 250 mg/l TSS (per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot drum filter flow requirement 101st 2024
drum.flowplot.101 <- cumulative.tss.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1") & !system %in% c("quarantine", "depurate")) %>%
  ggplot(aes(facility_day, process.drum.flow, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("nursery", "growout"),
                     values = c(system_cols),
                     labels = c("Nursery", "Growout")) +
  labs(x = "Day", y = expression(paste("Drum Filter ", (m^3/hr)))) + 
  theme_minimal()

drum.flowplot.101
```

Drum Filter Water Usage

Drum filter water usage calculations based upon 50 litres consumed for cleaning per kilo of feed supplied (under normal fish farm conditions). Adjusted here to reflect additional bacterial biomass produced under biofloc conditions.

### 95^th^ st. 2022

``` {r drum_useage_95}

# get drum water usage per day for each system 95th st 2022 (overlapping batches where appropriate)

# ignore the above and get a facility sum
drum.use.facility.95 <- cumulative.tss.95 %>%
  drop_na() %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.bf)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

# ignore the above and get a facility sum
drum.use.facility.cw.95 <- cumulative.tss.95 %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.cw)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

drum.facility.use.95 <-
  bind_cols(drum.use.facility.cw.95, drum.use.facility.95)

# get drum water usage for individual system processes 95th st 2022
drum.use.process.95 <- cumulative.tss.95 %>%
  drop_na() %>%
  group_by(system) %>%
  summarise(drum.use.p.max = max(process.drum.water.use.bf),
            drum.use.p.avg = mean(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get drum water usage for individual system processes 95th st 2022
drum.use.process.cw.95 <- cumulative.tss.95 %>%
  group_by(system) %>%
  summarise(drum.use.p.max = max(process.drum.water.use.cw),
            drum.use.p.avg = mean(process.drum.water.use.cw)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join drum water usage summary tibbles 95th st 2022
drum.use.summary.combined.95 <- left_join(drum.use.process.cw.95,
                                 drum.use.process.95,
                                 by = "system") %>%
  filter(!system %in% c("quarantine", "depurate"))
```

``` {r FacilityDrumUseTable95, ft.align = "center"}

drum.facility.use.95 %>%
  flextable() %>%
  set_header_labels(drum.use.s.max...1 = "Max Volume CW", drum.use.s.avg...2 = "Avg Volume CW", drum.use.s.max...3 = "Max Volume BF", drum.use.s.avg...4 = "Avg Volume BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Estimated facility drum filter water use m", as_sup("3"), "/day (clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r DrumUseageTable95, ft.align = "center"}

drum.use.summary.combined.95 %>%
  flextable() %>%
  set_header_labels(system = "System", drum.use.p.max.x = "Max Use CW", drum.use.p.avg.x = "Avg Use CW", drum.use.p.max.y = "Max Use BF", drum.use.p.avg.y = "Avg Use BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System drum filter water use m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 95^th^ st. 2023

``` {r drum_usage_primo}

# get drum water usage  for each system 95th st 2023 (overlapping batches where appropriate)

# ignore the above and get a facility sum
drum.use.facility.primo <- cumulative.tss.primo %>%
  drop_na() %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.bf)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

# ignore the above and get a facility sum
drum.use.facility.cw.primo <- cumulative.tss.primo %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.cw)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

drum.facility.use.primo <-
  bind_cols(drum.use.facility.cw.primo, drum.use.facility.primo)

# get drum water usage for individual system processes 95th st 2022
drum.use.process.primo <- cumulative.tss.primo %>%
  drop_na() %>%
  group_by(system) %>%
  summarise(drum.use.p.max = max(process.drum.water.use.bf),
            drum.use.p.avg = mean(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get drum water usage for individual system processes 95th st 2022
drum.use.process.cw.primo <- cumulative.tss.primo %>%
  group_by(system) %>%
  summarise(drum.use.p.max = max(process.drum.water.use.cw),
            drum.use.p.avg = mean(process.drum.water.use.cw)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join drum water usage summary tibbles 95th st 2022
drum.use.summary.combined.primo <- left_join(drum.use.process.cw.primo,
                                 drum.use.process.primo,
                                 by = "system") %>%
  filter(!system %in% c("quarantine", "depurate"))

# get drum water usage for individual system processes 95th st 2023
```

``` {r FacilityDrumUseTablePrimo, ft.align = "center"}

drum.facility.use.primo %>%
  flextable() %>%
  set_header_labels(drum.use.s.max...1 = "Max Use CW", drum.use.s.avg...2 = "Avg Use CW", drum.use.s.max...3 = "Max Use BF", drum.use.s.avg...4 = "Avg Use BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Estimated facility drum filter water use m", as_sup("3"), "/day (clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r DrumUseageTablePrimo, ft.align = "center"}

drum.use.summary.combined.primo %>%
  flextable() %>%
  set_header_labels(system = "System", drum.use.p.max.x = "Max Use CW", drum.use.p.avg.x = "Avg Use CW", drum.use.p.max.y = "Max Use BF", drum.use.p.avg.y = "Avg Use BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System drum filter water use m", as_sup("3"), "/day (clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 101^st^ st. 2024

``` {r drum_usage_101}

# get max drum water usage for each system 101th st 2024 (overlapping batches where appropriate)


# ignore the above and get a facility sum 101
drum.use.facility.101 <- cumulative.tss.101 %>%
  drop_na() %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.bf)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

# ignore the above and get a facility sum
drum.use.facility.cw.101 <- cumulative.tss.101 %>%
  filter(!system %in% c("quarantine", "depurate")) %>%
  group_by(facility_day) %>%
  summarise(total.drum.use.sum = sum(total.drum.water.use.cw)) %>%
  summarise(drum.use.s.max = max(total.drum.use.sum),
            drum.use.s.avg = mean(total.drum.use.sum))

drum.facility.use.101 <-
  bind_cols(drum.use.facility.cw.101, drum.use.facility.101)


# get max drum water usage for individual system processes 101st st 2024 4 raceway batch
drum.use.process.101a <- cumulative.tss.101 %>%
  drop_na() %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(drum.use.p.max.a = max(process.drum.water.use.bf),
            drum.use.p.avg.a = mean(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max drum water usage for individual system processes 101st st 2024 6 raceway batch
drum.use.process.101b <- cumulative.tss.101 %>%
  drop_na() %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(drum.use.p.max.b = max(process.drum.water.use.bf),
            drum.use.p.avg.b = mean(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join drum water usage summary tibbles 101st st 2024
drum.use.summary.101 <- left_join(drum.use.process.101a,
                                  drum.use.process.101b,
                                  by = "system") %>% 
  filter(!system %in% c("quarantine", "depurate"))

# get max drum water usage for individual system processes 101st st 2024 4 raceway batch CW
drum.use.process.cw.101a <- cumulative.tss.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(drum.use.p.max.a = max(process.drum.water.use.cw),
            drum.use.p.avg.a = mean(process.drum.water.use.cw)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max drum water usage for individual system processes 101st st 2024 6 raceway batch
drum.use.process.cw.101b <- cumulative.tss.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(drum.use.p.max.b = max(process.drum.water.use.cw),
            drum.use.p.avg.b = mean(process.drum.water.use.cw)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join drum water usage summary tibbles 101st st 2024
drum.use.summary.cw.101 <- left_join(drum.use.process.cw.101a,
                                  drum.use.process.cw.101b,
                                  by = "system") %>% 
  filter(!system %in% c("quarantine", "depurate"))
```

``` {r FacilityDrumUseTable101, ft.align = "center"}

drum.facility.use.101 %>%
  flextable() %>%
  set_header_labels(drum.use.s.max...1 = "Max Use CW", drum.use.s.avg...2 = "Avg Use CW", drum.use.s.max...3 = "Max Use BF", drum.use.s.avg...4 = "Avg Use BF") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility drum filter water use m", as_sup("3"), "/day (clearwater CW and biofloc BF)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r DrumUsageTableCW101, ft.align = "center"}

drum.use.summary.cw.101 %>%
  flextable() %>%
  set_header_labels(system = "System", drum.use.p.max.a = "Max Use A", drum.use.p.avg.a = "Avg Use A", drum.use.p.max.b = "Max Use B", drum.use.p.avg.b = "Avg Use B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Estimated system drum filter water use (as clearwater system) m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r DrumUsageTable101, ft.align = "center"}

drum.use.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", drum.use.p.max.a = "Max Use A", drum.use.p.avg.a = "Avg Use A", drum.use.p.max.b = "Max Use B", drum.use.p.avg.b = "Avg Use B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Estimated system drum filter water use (as biofloc system) m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r drum_sum_95}

# calculate sum of drum filter water use across system/ batch 95th st 2022
drum.sum.95 <- cumulative.tss.95 %>%
  drop_na() %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(drum.sum = sum(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))
```

``` {r drum_sum_primo}

# calculate sum of drum filter water use across system/ batch 95th st 2023
drum.sum.primo <- cumulative.tss.primo %>%
  drop_na() %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(drum.sum = sum(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))
```

``` {r drum_sum_101}

# calculate sum of drum filter water use across system/ batch 101st st 2024 4 tank strategy
drum.sum.101.a <- cumulative.tss.101 %>%
  drop_na() %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(drum.sum = sum(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# calculate sum of drum filter water use across system/ batch 101st st 2024 6 tank strategy
drum.sum.101.b <- cumulative.tss.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(drum.sum = sum(process.drum.water.use.bf)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))
```

***

## Oxygen

Oxygen demand - for specification of emergency oxygen requirements/ oxygen supply systems or air supply volume (air volumes estimated with a 5% oxygen transfer efficiency rate)

### 95^th^ st. 2022.

``` {r oxygen_demand_95}

# get max oxygen demand for each system 95th st 2022 (overlapping batches where appropriate)
oxy.system.95 <- system.parameters.95 %>%
  group_by(system, facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and get facility loading
oxy.facility.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum))

# get max oxygen demand for individual system processes 95th st 2022
oxy.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(oxy.p.max = max(process.od),
            oxy.p.avg = mean(process.od)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

air.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(oxy.p.max = max(process.od / (0.26 * 0.05)),
            oxy.p.avg = mean(process.od / (0.26 * 0.05))) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join oxygen demand summary tibbles 95th st 2022
oxy.summary.95 <- left_join(oxy.system.95, oxy.process.95, by = "system")
```

``` {r FacilityOxyUseTable95, ft.align = "center"}

oxy.facility.95 %>%
  flextable() %>%
  set_header_labels(oxy.s.max = "Max oxy", oxy.s.avg = "Avg oxy") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility oxygen requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r OdTable95, ft.align = "center"}

oxy.process.95 %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max = "System max OD", oxy.p.avg = "System avg OD") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System oxygen demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AirTable95, ft.align = "center"}

air.process.95 %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max = "Max air demand", oxy.p.avg = "Avg air demand") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System air demand to supply required oxygen m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 95^th^ st. 2023.

``` {r oxygen_demand_primo}

# get max oxygen demand for each system 95th st 2023 (overlapping batches where appropriate)
oxy.system.primo <- system.parameters.primo %>%
  group_by(system, facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and get facility loading
oxy.facility.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum))

# get max oxygen demand for individual system processes 95th st 2023
oxy.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(oxy.p.max = max(process.od),
            oxy.p.avg = mean(process.od)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

air.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(oxy.p.max = max(process.od / (0.26 * 0.05)),
            oxy.p.avg = mean(process.od / (0.26 * 0.05))) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join oxygen demand summary tibbles 95th st 2023
oxy.summary.primo <- left_join(oxy.system.primo, oxy.process.primo, by = "system")
```

``` {r FacilityOxyUseTablePrimo, ft.align = "center"}

oxy.facility.primo %>%
  flextable() %>%
  set_header_labels(oxy.s.max = "Max oxy", oxy.s.avg = "Avg oxy") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Facility oxygen requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r OdTablePrimo, ft.align = "center"}

oxy.process.primo %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max = "System max OD", oxy.p.avg = "System avg OD") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System oxygen demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AirTablePrimo, ft.align = "center"}

air.process.primo %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max = "Max air demand", oxy.p.avg = "Avg air demand") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System air demand to supply required oxygen m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 101^st^ st. 2024.

``` {r oxygen_demand_101}

# get max oxygen demand loading for each system 101th st 2024 (overlapping batches where appropriate)
oxy.system.101 <- system.parameters.101 %>%
  group_by(system, facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and get facility loading
oxy.facility.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(oxy.sum = sum(total.od)) %>%
  summarise(oxy.s.max = max(oxy.sum),
            oxy.s.avg = mean(oxy.sum))

# get max oxygen demand loading for individual system processes 101st st 2024 4 raceway batch
oxy.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(oxy.p.max.a = max(process.od),
            oxy.p.avg.a = mean(process.od)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max oxygen demand loading for individual system processes 101st st 2024 6 raceway batch
oxy.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(oxy.p.max.b = max(process.od),
            oxy.p.avg.b = mean(process.od)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

air.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(oxy.p.max.a = max(process.od) / (0.26 * 0.05),
            oxy.p.avg.a = mean(process.od) / (0.26 * 0.05)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

air.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(oxy.p.max.b = max(process.od) / (0.26 * 0.05),
            oxy.p.avg.b = mean(process.od) / (0.26 * 0.05)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join oxygen demand summary tibbles 101st st 2024
oxy.summary.101 <- left_join(oxy.process.101a, oxy.process.101b, by = "system")

air.summary.101 <- left_join(air.process.101a, air.process.101b, by = "system")
```

``` {r FacilityOxyUseTable101, ft.align = "center"}

oxy.facility.101 %>%
  flextable() %>%
  set_header_labels(oxy.s.max = "Max oxy", oxy.s.avg = "Avg oxy") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility oxygen requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r OdTable101, ft.align = "center"}

oxy.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max.a = "System max OD A", oxy.p.avg.a = "System avg OD A", oxy.p.max.b = "System max OD B", oxy.p.avg.b = "System avg OD B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System oxygen demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AirTable101, ft.align = "center"}

air.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", oxy.p.max.a = "Max air demand A", oxy.p.avg.a = "Avg air demand", oxy.p.max.b = "Max air demand B", oxy.p.avg.b = "Avg air demand B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System air demand to supply required oxygen m", as_sup("3"), "/day."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

***

## Alkalinity

For every g of ammonia-nitrogen converted to nitrate-nitrogen (chemoautotrophic pathway), 7.05 g of alkalinity (1.69 g inorganic carbon) is consumed.

For every g of ammonia-nitrogen converted to microbial biomass (heterotrophic pathway), 3.57 g of alkalinity (0.86 g inorganic carbon) is consumed.

Alkalinity also plays a role in pH buffering capacity

The following tables indicate the average and maximum alkalinity demands and will be followed by charts predicting daily alkalinity consumption in tanks/ process units.

### 95^th^ st. 2022

``` {r alkalinity_demand_95}

# get max alkalinity demand for each system 95th st 2022 (overlapping batches where appropriate)
alk.system.95 <- system.parameters.95 %>%
  group_by(system, facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility requirement
alk.facility.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum))

# get max alkalinity demand for individual system processes 95th st 2022
alk.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(alk.p.max = max(process.alk),
            alk.p.avg = mean(process.alk)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join alkalinity demand summary tibbles 95th st 2022
alk.summary.95 <- left_join(alk.system.95, alk.process.95, by = "system")
```

``` {r FacilityAlkDemandTable95, ft.align = "center"}

alk.facility.95 %>%
  flextable() %>%
  set_header_labels(alk.s.max = "Max Alk", alk.s.avg = "Avg Alk") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility alkalinity requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkDemandTable95, ft.align = "center"}

alk.process.95 %>%
  flextable() %>%
  set_header_labels(system = "System", alk.p.max = "System max Alk", alk.p.avg = "System avg Alk") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System alkalinity demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkProfile95, fig.cap = "95^th^ st. 2022 Theoretical supplimentary alkalinity requirement (kg per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot alkalinity requirement across batch run 95th st 2022
tank.alk.95 <- system.parameters.95 %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.alk, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = "Supplimentary alkalinity required (kg per day)") + 
  theme_minimal()

tank.alk.95
```

### 95^th^ st. 2023

``` {r alkalinity_demand_primo}

# get max alkalinity demand for each system 95th st 2023 (overlapping batches where appropriate)
alk.system.primo <- system.parameters.primo %>%
  group_by(system, facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility requirement
alk.facility.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum))

# get max alkalinity demand for individual system processes 95th st 2023
alk.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(alk.p.max = max(process.alk),
            alk.p.avg = mean(process.alk)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join alkalinity demand summary tibbles 95th st 2023
alk.summary.primo <- left_join(alk.system.primo, alk.process.primo, by = "system")
```

``` {r FacilityAlkDemandTablePrimo, ft.align = "center"}

alk.facility.primo %>%
  flextable() %>%
  set_header_labels(alk.s.max = "Max Alk", alk.s.avg = "Avg Alk") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Facility alkalinity requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkDemandTablePrimo, ft.align = "center"}

alk.process.primo %>%
  flextable() %>%
  set_header_labels(system = "System", alk.p.max = "System max Alk", alk.p.avg = "System avg Alk") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System alkalinity demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkProfilePrimo, fig.cap = "95^th^ st. 2023 Theoretical supplimentary alkalinity requirement (kg per System).", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot alkalinity requirement across batch run 95th st 2023
tank.alk.primo <- system.parameters.primo %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, process.alk, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery","Growout", "Depurate")) +
  labs(x = "Day", y = "Supplimentary alkalinity required (kg per day)") + 
  theme_minimal()

tank.alk.primo
```

### 101^st^ st. 2024

``` {r alkalinity_demand_101}

# get max alkalinity demand for each system 101th st 2024 (overlapping batches where appropriate)
alk.system.101 <- system.parameters.101 %>%
  group_by(system, facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore the above and get facility requirement
alk.facility.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(alk.sum = sum(total.alk)) %>%
  summarise(alk.s.max = max(alk.sum),
            alk.s.avg = mean(alk.sum))

# get max alkalinity demand for individual system processes 101st st 2024 4 raceway batch
alk.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(alk.p.max.a = max(process.alk),
            alk.p.avg.a = mean(process.alk)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max alkalinity demand for individual system processes 101st st 2024 6 raceway batch
alk.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(alk.p.max.b = max(process.alk),
            alk.p.avg.b = mean(process.alk)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join alkalinity demand summary tibbles 101st st 2024
alk.summary.101 <- left_join(alk.process.101a, alk.process.101b, by = "system")
```

``` {r FacilityAlkDemandTable101, ft.align = "center"}

alk.facility.101 %>%
  flextable() %>%
  set_header_labels(alk.s.max = "Max Alk", alk.s.avg = "Avg Alk") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility alkalinity requirement (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkDemandTable101, ft.align = "center"}

alk.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", alk.p.max.a = "System max Alk A", alk.p.avg.a = "System avg Alk A", alk.p.max.b = "System max Alk B", alk.p.avg.b = "System avg Alk B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System alkalinity demand (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r AlkProfile101, fig.cap = "101^st^ st. 2024 Theoretical supplimentary alkalinity requirement (kg per System.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot alkalinity requirement across batch run 101st st 2024
tank.alk.101 <- system.parameters.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1")) %>%
  ggplot(aes(facility_day, process.alk, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery","Growout", "Depurate")) +
  labs(x = "Day", y = "Supplimentary alkalinity required (kg per day)") + 
  theme_minimal()

tank.alk.101
```

***

## CO~2~

Literature suggests dissolved CO~2~ should remain below 7mg/l - 10mg/l

Tables below summarise daily CO~2~ production for overall facility and tank/ process units

### 95^th^ st. 2022

``` {r co2_produced_95}

# get max co2 produced for each system 95th st 2022 (overlapping batches where appropriate)
co2.system.95 <- system.parameters.95 %>%
  group_by(system, facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and calculate facility figure
co2.facility.95 <- system.parameters.95 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum))

# get max co2 produced for individual system processes 95th st 2022
co2.process.95 <- system.parameters.95 %>%
  group_by(system) %>%
  summarise(co2.p.max = max(process.co2),
            co2.p.avg = mean(process.co2)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join co2 produced summary tibbles 95th st 2022
co2.summary.95 <- left_join(co2.system.95, co2.process.95, by = "system")
```

``` {r FacilityCo2ProducedTable95, ft.align = "center"}

co2.facility.95 %>%
  flextable() %>%
  set_header_labels(co2.s.max = "Max Loading", co2.s.avg = "Avg Loading") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r Co2ProducedTable95, ft.align = "center"}

co2.process.95 %>%
  flextable() %>%
  set_header_labels(system = "System", co2.p.max = "Max Loading", co2.p.avg = "Avg Loading") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 System CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 95^th^ st. 2023

``` {r co2_produced_primo}

# get max co2 produced for each system 95th st 2023 (overlapping batches where appropriate)
co2.system.primo <- system.parameters.primo %>%
  group_by(system, facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and calculate facility figure
co2.facility.primo <- system.parameters.primo %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum))

# get max co2 produced for individual system processes 95th st 2023
co2.process.primo <- system.parameters.primo %>%
  group_by(system) %>%
  summarise(co2.p.max = max(process.co2),
            co2.p.avg = mean(process.co2)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join co2 produced summary tibbles 95th st 2023
co2.summary.primo <- left_join(co2.system.primo, co2.process.primo, by = "system")
```

``` {r FacilityCo2ProducedTablePrimo, ft.align = "center"}

co2.facility.primo %>%
  flextable() %>%
  set_header_labels(co2.s.max = "Max Loading", co2.s.avg = "Avg Loading") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 Facility CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r Co2ProducedTablePrimo, ft.align = "center"}

co2.process.primo %>%
  flextable() %>%
  set_header_labels(system = "System", co2.p.max = "Max Loading", co2.p.avg = "Avg Loading") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2023 System CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

### 101^st^ st. 2024

``` {r co2_produced_101}

# get max co2 produced for each system 101th st 2024 (overlapping batches where appropriate)
co2.system.101 <- system.parameters.101 %>%
  group_by(system, facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# ignore above and calculate facility figure
co2.facility.101 <- system.parameters.101 %>%
  filter(!system == "quarantine") %>%
  group_by(facility_day) %>%
  summarise(co2.sum = sum(total.co2)) %>%
  summarise(co2.s.max = max(co2.sum),
            co2.s.avg = mean(co2.sum))

# get max co2 produced for individual system processes 101st st 2024 4 raceway batch
co2.process.101a <- system.parameters.101 %>%
  filter(batch == "lag.batch.0") %>%
  group_by(system) %>%
  summarise(co2.p.max.a = max(process.co2),
            co2.p.avg.a = mean(process.co2)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# get max co2 produced for individual system processes 101st st 2024 6 raceway batch
co2.process.101b <- system.parameters.101 %>%
  filter(batch == "lag.batch.1") %>%
  group_by(system) %>%
  summarise(co2.p.max.b = max(process.co2),
            co2.p.avg.b = mean(process.co2)) %>%
  arrange(factor(system, levels = c("quarantine", "nursery", "juvenile", "growout", "depurate")))

# join co2 produced summary tibbles 101st st 2024
co2.summary.101 <- left_join(co2.process.101a, co2.process.101b, by = "system")
```

``` {r FacilityCo2ProducedTable101, ft.align = "center"}

co2.facility.101 %>%
  flextable() %>%
  set_header_labels(co2.s.max = "Max Loading", co2.s.avg = "Avg Loading") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 Facility CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r Co2ProducedTable101, ft.align = "center"}

co2.summary.101 %>%
  flextable() %>%
  set_header_labels(system = "System", co2.p.max.a = "Max Loading A", co2.p.avg.a = "Avg Loading A", co2.p.max.b = "Max Loading B", co2.p.avg.b = "Avg Loading B") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("101", as_sup("st"), " st. 2024 System CO", as_sub("2"), " loading (Kg/day)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

Flow requirements to maintain CO~2~ levels at a maximum of 10mg/l (for pH values above 7.5 with alkalinity ~ 150 mg/l, no degassing required, aeration expected to prevent buildup of CO~2~) 

### 95^th^ st. 2022

``` {r co2_flow_95}

# get flow requirement to degas tanks 95th st 2022
co2.flow.95 <- system.parameters.95 %>%
  mutate(c02.flow = abs(process.co2 * 1e6 / (co2.c2 - co2.c1) / 24 / 1000))
```

``` {r Co2FlowPlot95, fig.cap = "95^th^ st. 2022 System flow rate required to degas CO~2~ to 10 mg/l.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot co2 flow requirement across batch run 95th st 2022
tank.co2.95 <- co2.flow.95 %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, c02.flow, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = expression(paste("Flow to maintain ", CO[2], " at 10 mg/l ", (m^3/hr)))) + 
  theme_minimal()

tank.co2.95
```

### 95^th^ st. 2023

``` {r co2_flow_primo}

# get flow requirement to degas tanks 95th st 2023
co2.flow.primo <- system.parameters.primo %>%
  mutate(c02.flow = abs(process.co2 * 1e6 / (co2.c2 - co2.c1) / 24 / 1000))
```

``` {r Co2FlowPlotPrimo, fig.cap = "95^th^ st. 2023 System flow rate required to degas CO~2~ to 10 mg/l.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot co2 flow requirement across batch run 95th st 2023
tank.co2.primo <- co2.flow.primo %>%
  filter(batch == "lag.batch.0") %>%
  ggplot(aes(batch_day, c02.flow, color = system)) +
  geom_line()+
  scale_color_manual("", breaks = c("quarantine", "nursery", "juvenile", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery", "Juvenile", "Growout", "Depurate")) +
  labs(x = "Day", y = expression(paste("Flow to maintain ", CO[2], " at 10 mg/l ", (m^3/hr)))) + 
  theme_minimal()

tank.co2.primo
```

### 101^st^ st. 2024

``` {r co2_flow_101}

# get flow requirement to degas tanks 101st st 2024
co2.flow.101 <- system.parameters.101 %>%
  mutate(c02.flow = abs(process.co2 * 1e6 / (co2.c2 - co2.c1) / 24 / 1000))
```

``` {r Co2FlowPlot101, fig.cap = "101^st^ st. 2024 System flow rate required to degas CO~2~ to 10 mg/l.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot co2 flow requirement across batch run 101st st 2024
tank.co2.101 <- co2.flow.101 %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.1")) %>%
  ggplot(aes(facility_day, c02.flow, color = system)) +
  geom_line()+
  facet_wrap(~batch, ncol = 1, labeller = as_labeller(batch.names)) +
  scale_color_manual("", breaks = c("quarantine", "nursery", "growout", "depurate"),
                     values = c(system_cols),
                     labels = c("Quarantine", "Nursery","Growout", "Depurate")) +
  labs(x = "Day", y = expression(paste("Flow to maintain ", CO[2], " at 10 mg/l ", (m^3/hr)))) + 
  theme_minimal()

tank.co2.101
```

***

# Summary Charts of Water Chemsitry Data RW4 95^th^ st. 2022

```{r water_chem_data_import}

# import data
water_chem <- read.csv("data/water_chem.csv")

rainfall <- read.csv("data/rain_aet.csv") %>%
  mutate(date = as.Date(date))

primo.water <- read.csv("data/primo_water_21.csv")
```

``` {r water_chem_data_clean}

# clean up spreadsheet
water_chem <- water_chem %>%
  mutate(DATE = as.Date(DATE, origin = "1899-12-30"),
         pH = as.numeric(str_replace(pH, "-", "")),
         Tempmax = str_replace(Tempmax, "-", ""),
         Tempmax = as.numeric(str_replace(Tempmax, ",", ".")),
         Feed = as.numeric(str_remove_all(Feed, "[:alpha:]|\\s")),
         Solids = as.numeric(str_remove_all(Solids, "[:alpha:]|\\s|\\(|\\)|\\-")),
         Settling.Tank = str_to_lower(Settling.Tank),
         Foam.Level = as.numeric(str_remove_all(Foam.Level, "[:alpha:]|\\/|\\s")))
```

``` {r water_chem_data_mutate}

# mutate some useful parameters
water_chem_4 <- water_chem %>%
  filter(DATE > "2021-12-31") %>%
  mutate(batch = case_when(DATE < "2022-02-17" ~ "batch_1",
                           DATE >= "2022-02-17" & DATE <= "2022-08-18" ~ "batch_2",
                           DATE >= "2022-08-20" & DATE <= "2022-11-30" ~ "batch_3"),
         total.feed = Feed * 8,
         Nitrite = case_when(Nitrite > 100 ~ Nitrite / 1000,
                             TRUE ~ Nitrite),
         pH = replace(pH, pH > 14, NA_real_),
         Settling.Tank = case_when(Settling.Tank == "no" ~ 0,
                                   Settling.Tank == "yes" ~ 1,
                                   TRUE ~ 0),
         pka = 0.0901821 + 2729.92/(Tempmin + 273.15),
         ionic.strength = 19.9273 * Salinity / (1000 - 1.005109 * Salinity),
         pkas = pka + (0.1552 - 0.000314 * Tempmin) * ionic.strength,
         mole.fraction = 1 / (1 + 10^(pkas - pH)),
         free.ammonia = TAN * mole.fraction)


```

## TAN Levels RW4 2022

``` {r rw4Tan, fig.cap = "TAN levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot TAN
rw_4_tan <- water_chem_4 %>%
  ggplot(aes(DATE, TAN, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "TAN (mg/l)") + 
  theme_minimal()

rw_4_tan
```

Comments: Sub-optimal variation in TAN levels, indication of variable rate of ammonia removal. Majority of time TAN is within acceptable level < 1.0 mg/l. Consider organic carbon addition according to feed protein loading to maintain a steady state carbon source for bacteria to process ammonia. 

## Unionised Ammonia

``` {r rw4ammonia, fig.cap = "Free ammonia levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot free ammonia
rw_4_free.nh4 <- water_chem_4 %>%
  ggplot(aes(DATE, free.ammonia, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Free Ammonia (mg/l)") + 
  theme_minimal()

rw_4_free.nh4
```

Comments: High variability in level of unionised ammonia. Influenced by both TAN and pH. Instances of levels exceeding 0.3mg/l, majority of time within acceptable range.

## Nitrite RW4 2022

``` {r rw4Nitrite, fig.cap = "Nitrite levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot nitrite
rw_4_nit <- water_chem_4 %>%
  ggplot(aes(DATE, Nitrite, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Nitrite (mg/l)") + 
  theme_minimal()

rw_4_nit
```

Comments. For a heterotrophic managed nitrogen removal system, production of nitrite expected to be low (realistically a small proportion of ammonia will be converted to nitrite and nitrate by the autotrophic pathway). Management of optimal C:N ratio and solids removal to optimise heterotrophic domination of ammonia removal.

## Alkalinity RW4 2022

``` {r rw4Alk, fig.cap = "Alkalinity levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot Alk
rw_4_alk <- water_chem_4 %>%
  ggplot(aes(DATE, ALK, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Alkalinity (mg/l)") + 
  theme_minimal()

rw_4_alk
```

Comments: Alkalinity appears to be well managed.

## pH RW4 2022

``` {r rw4ph, fig.cap = "pH levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot pH
rw_4_ph <- water_chem_4 %>%
  ggplot(aes(DATE, pH, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "pH") + 
  theme_minimal()

rw_4_ph
```

Comments: High variability in pH level (bearing in mind pH is an on exponential scale). pH influences proportion of unionised:ionised ammonia. Consider pH management techniques (alkalinity & pH dosing system)

## Salinity RW4 2022

``` {r rw4Salinity, fig.cap = "Salinity levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot salinity
rw_4_sal <- water_chem_4 %>%
  ggplot(aes(DATE, Salinity, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Salinity (ppt)") + 
  theme_minimal()

rw_4_sal
```

Comments: Salinity appears to be well managed

## Dissolved Oxygen RW4 2022

``` {r rw4Oxygen, fig.cap = "Dissolved oxygen levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot DO
rw_4_do <- water_chem_4 %>%
  ggplot(aes(DATE, DOmin, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "DO min (mg/l)") + 
  theme_minimal()

rw_4_do
```

Comments: Oxygen levels appear to be higher during the first half of the production year. All values within acceptable range > 5mg/l

## Solids RW4 2022

``` {r rw4Solids, fig.cap = "Solids levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot solids
rw_4_solids <- water_chem_4 %>%
  ggplot(aes(DATE, Solids, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Solids (ml)") + 
  theme_minimal()

rw_4_solids
```

Comments: High range of solids variability. Lack of knowledge on how to interpret volume of solids in imhoff cone in terms of TSS. Further sample analysis required to achieve this and then define an acceptable operating range. 

## Settling Tank Operation RW4 2022

``` {r rw4Settling, fig.cap = "Settling tank operation in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot settling tank
rw_4_settling <- water_chem_4 %>%
  ggplot(aes(DATE, Settling.Tank, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Settling Tank (1/0)") + 
  theme_minimal()

rw_4_settling
```

Comments : During 2022 the settling tank in RW4 was operated for a total of `r sum(water_chem_4$Settling.Tank)` days from a production period of `r length(water_chem_4$Settling.Tank)` days. Total discharge water from this settling tank was `r sum(water_chem_4$Settling.Tank) * 2` m^3^. Average water use for solids removal from RW4 `r format(sum(water_chem_4$Settling.Tank) * 2 / length(water_chem_4$Settling.Tank), digits = 3)` m^3^/day. 

Settling tank operation appears to be determined by reaching a maximum permitted level of solids in the imhoff cone. Suggest optimisation by having a smaller permitted range of solids, achieve by more frequent use of settling vessel (consider volume and flow rate accordingly). Pumping water into a settling tank will incur mechanical disruption, reduce particle size and efficiency of settlement device - avoid unless unfeasible.Decrease inlet water velocity as far as possible, without permitting settlement within pipework. Density of waste should be determined for correct calculation of settlement rate/ flow in settlement tank.

## Total Feed Input RW4 2022

``` {r rw4Feed, fig.cap = "Total daily feed input in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot total feed
rw_4_feed <- water_chem_4 %>%
  ggplot(aes(DATE, total.feed / 1000, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Total Feed (kg)") + 
  theme_minimal()

rw_4_feed
```

## Estimated Nitrate levels bsed on cumulative Nitrite calculation

``` {r rw4_cumulative_nitrate}

# estimate cumulative nitrate based on nitrite production
cumulative.nitrate.95 <- water_chem_4 %>%
  mutate(total.volume = raceway.tank * 1000 * Water.Level / 36,
         total.nitrite = Nitrite * total.volume) %>%
  group_by(batch) %>%
  mutate(cs = cumsum(total.nitrite),
         cumulative.nitrate = cs / total.volume)
```

``` {r rw4Nitrate, fig.cap = "Estimated nitrate levels in RW 4 2022.", fig.align = "center", fig.dim = c(8,3), dpi = 200}

# plot cumulative nitrate
rw_4_nitrate <- cumulative.nitrate.95 %>%
  ggplot(aes(DATE, cumulative.nitrate, color = batch)) +
  geom_line()+
  scale_color_manual("", breaks = c("batch_1", "batch_2", "batch_3"),
                     values = c("#d0d1e6", "#a6bddb", "#74a9cf"),
                     labels = c("Batch 1", "Batch 2", "Batch 3")) +
  labs(x = "Date", y = "Cumulative Nitrate (mg/l)") + 
  theme_minimal()

rw_4_nitrate
```

Comments: Accumulation of nitrate has been calculated based on assumption of water discharged at end of a batch. Under these conditions nitrate appears to remain within acceptable levels. Consider periodic monitoring of nitrate to confirm this.

## Rainfall / Evapo-transpiration Blue Cypress Lake

``` {r RainfallPlot, fig.cap = "Mean monthly precipitation/ evapo-transpiration rates for Blue Cypress Lake, Florida, USA.", fig.align = "center", fig.dim = c(8,3), dpi = 200}
# custom color
rain.cols <- c(rainfall = "#a6bddb", aet = "#045a8d")

rainfall %>%
  ggplot(aes(date, measure_in, color = condition)) +
  geom_line() +
  scale_color_manual("", breaks = c("rainfall", "aet"),
                     values = c(rain.cols),
                     labels = c("Rainfall", "AET")) +
  labs(x = "Date", y = "Precipitation/ Evapo-transpiration (Inches)") + 
  theme_minimal()
```

Comments: Generally, precipitation greater than evapotranspiration - not favourable for removal of discharge water by evaporation.

## 95^th^ st. 2022 Water Budget

``` {r water_budget_2022}

# set production period to two growth periods to observe system loading
prod.plan_water <- data.frame(facility_day = seq(0, 365 - 1)) %>%
  mutate(batch_1 = case_when(facility_day < 365 ~ facility_day))

for (lag_size in c(0:12)) {
  
  new_col_name <- paste0("lag.batch.", lag_size)
  
  prod.plan_water <- prod.plan_water %>%
    mutate(!!sym(new_col_name) := lag(batch_1, n = lag_size * batch_frequency, default = NA))
}

# remove column called batch_1
prod.plan.water <- prod.plan_water %>% select(-batch_1) %>%
  pivot_longer(c(lag.batch.0:lag.batch.12), names_to = "batch", values_to = "batch_day", values_drop_na = TRUE) %>%
  mutate(system = case_when(batch_day %in% c(0:quarantine.period) ~ "quarantine",
                            batch_day %in% c(quarantine.period + 1: nursery.period) ~ "nursery",
                            batch_day %in% c(quarantine.period + nursery.period + 1 : juvenile.period) ~ "juvenile",
                            batch_day %in% c(quarantine.period + nursery.period + juvenile.period + 1 : growout.period) ~ "growout",
                            batch_day %in% c(quarantine.period + nursery.period + juvenile.period + growout.period + 1 : depuration.period)  ~ "depurate",
                            TRUE ~ "harvested")) %>%
  drop_na() %>%
  filter(batch %in% c("lag.batch.0", "lag.batch.2", "lag.batch.5", "lag.batch.7", "lag.batch.10")) %>%
  mutate(water.management = case_when(batch_day == 29 ~ nursery.tank * nursery.system.division,
                                      batch_day == 59 ~ raceway.tank - nursery.tank * nursery.system.division,
                                      batch_day == 89 ~ raceway.tank,
                                      batch_day == 151 ~ raceway.tank * growout.system.division * 0.1,
                                      batch_day == 165 ~ raceway.tank * growout.system.division * 0.1,
                                      batch_day == 167 ~ purging.unit,
                                      batch_day == 169 ~ packing.volume * growout.system.division,
                                      batch_day == 179 ~ raceway.tank * growout.system.division * 0.1,
                                      batch_day == 183 ~ packing.volume * growout.system.division,
                                      batch_day == 193 ~ raceway.tank * growout.system.division * 0.1,
                                      batch_day == 199 ~ 53 /3 * 2 * growout.system.division,
                                      TRUE ~ 0),
         water.management = case_when(facility_day == 32 & batch == "lag.batch.0" ~ 198,
                                      facility_day == 62  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 90  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 120  & batch == "lag.batch.0" ~ 198,
                                      facility_day == 150  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 180  & batch == "lag.batch.0" ~ 182,
                                      facility_day == 212  & batch == "lag.batch.0" ~ 198,
                                      facility_day == 242  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 272  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 304  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 334  & batch == "lag.batch.0" ~ 236,
                                      facility_day == 364  & batch == "lag.batch.0" ~ 220,
                                      TRUE ~ water.management),
         water.designation = case_when(facility_day == 32 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 62 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 90 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 120 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 150 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 180 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 212 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 242 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 272 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 304 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 334 & batch == "lag.batch.0" ~ "delivery",
                                       facility_day == 364 & batch == "lag.batch.0" ~ "delivery",
                                       TRUE ~ "required"),
         water.management.drum = case_when(batch_day == 29 ~ nursery.tank * nursery.system.division,
                                           batch_day == 59 ~ raceway.tank - nursery.tank * nursery.system.division,
                                           batch_day == 61 ~ as.numeric(drum.sum.95[2,2]) * nursery.system.division,
                                           batch_day == 89 ~ raceway.tank,
                                           batch_day == 91 ~ as.numeric(drum.sum.95[3,2]) * juvenile.system.division,
                                           batch_day == 151 ~ raceway.tank * growout.system.division * 0.1,
                                           batch_day == 165 ~ raceway.tank * growout.system.division * 0.1,
                                           batch_day == 167 ~ purging.unit,
                                           batch_day == 169 ~ packing.volume * growout.system.division,
                                           batch_day == 179 ~ raceway.tank * growout.system.division * 0.1,
                                           batch_day == 183 ~ packing.volume * growout.system.division,
                                           batch_day == 193 ~ raceway.tank * growout.system.division * 0.1,
                                           batch_day == 201 ~ as.numeric(drum.sum.95[4,2]) * growout.system.division,
                                           TRUE ~ 0),
         water.management.drum = case_when(facility_day == 32 & batch == "lag.batch.0" ~ 198,
                                      facility_day == 62  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 90  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 120  & batch == "lag.batch.0" ~ 198,
                                      facility_day == 150  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 180  & batch == "lag.batch.0" ~ 182,
                                      facility_day == 212  & batch == "lag.batch.0" ~ 198,
                                      facility_day == 242  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 272  & batch == "lag.batch.0" ~ 213,
                                      facility_day == 304  & batch == "lag.batch.0" ~ 152,
                                      facility_day == 334  & batch == "lag.batch.0" ~ 236,
                                      facility_day == 364  & batch == "lag.batch.0" ~ 220,
                                      TRUE ~ water.management.drum))
```

### Summary of Water Use 2022

``` {r water_use_2022}

# from water production plan summarise delivered water verses expected requirements
water.use.2022 <- prod.plan.water %>%
  group_by(facility_day) %>%
  group_by(water.designation) %>%
  summarise(water.sum = sum(water.management))
```

``` {r WaterUse2022, ft.align = "center"}

water.use.2022 %>%
  flextable() %>%
  set_header_labels(water.designation = "Status", water.sum = "Volume") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Facility saltwater budget (m", as_sup("3"), " /year)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r water_projection_drum_2022}

# from water production plan summarise delivered water verses expected requirements if a drum filter were used instead of settlement tank
water.use.drum.2022 <- prod.plan.water %>%
  group_by(facility_day) %>%
  group_by(water.designation) %>%
  summarise(water.sum.drum = sum(water.management.drum))
```

``` {r WaterProjectionTable, ft.align = "center"}

water.use.drum.2022 %>%
  flextable() %>%
  set_header_labels(water.designation = "Status", water.sum.drum = "Volume") %>%
  colformat_double(digits = 2) %>%
  autofit() %>%
  fit_to_width(7.5) %>%
set_caption(caption = as_paragraph("95", as_sup("th"), " st. 2022 Projected Facility saltwater budget (with drum filter use) (m", as_sup("3"), " /year)."), 
  style = "Table Caption", 
  autonum = run_autonum(seq_id = "tab"))
```

``` {r cumulative_water_budget_2022}

# cumulative sum of water requirements and water delivered
prod.plan.water.cs <- prod.plan.water %>%
  group_by(water.designation) %>%
  mutate(water.cs = cumsum(water.management))
```

``` {r CumulativeWaterBudgetPlot2022, fig.cap = "Cumulative water delivery and expected water requirements 95^th^ st. 2022", fig.align = "center", fig.dim = c(8,3), dpi = 200}


water.budget.plot.2022 <- prod.plan.water.cs %>%
  ggplot(aes(facility_day, water.cs, color = water.designation)) +
  geom_line() +
  scale_color_manual("", breaks = c("delivery", "used"),
                     values = c("#d0d1e6", "#74a9cf"),
                     labels = c("Delivery", "Used")) +
  labs(x = "Day", y = expression(paste("Water Volume ", (m^3)))) + 
  theme_minimal()

water.budget.plot.2022
```

Total discharge water 2022 (95^th^ st. delivered to 101^st^ st) 798 m^3^

Comments: Water requirement appears to follow same gradient as water delivery. Discharge water volume appears to be low in comparison to water delivered/ used. Confirm.


